\documentclass[char]{Pestilence}
\begin{document}
\name{\cApprentice{}}

You were a disappointment the moment you were born. An elder traditionally bore one child to pass on their powers to and focused the rest of their attention on their duty. Unfortunately, despite your powerful parents, you barely had enough spiritual power to be distinguishable from a patch of cow hide. \cElder{\Parent} could not pass on \cElder{\their} powers to you, and consequently, \cRebel{} had to come into existence.

You liked \cRebel{} when \cRebel{\they} was a child. \cRebel{\They} looked up to you and listened to you, and you humored \cRebel{\them} by playing \cRebel{\their} odd games or helping with \cRebel{\their} schoolwork. You miss those simpler times sometimes. All is past, however. \cRebel{} is now an annoying little brat who constantly talks about how morally superior \cRebel{\they} is to everyone in town, even as \cRebel{\they} dabbles in blood magic and risks driving your family name to the ground. You told \cRebel{\them} to scram and left town the moment \cRebel{\they} had the gall to ask if you would help \cRebel{\them}. You couldn't bear to deal with your family then. \cRebel{} practiced blood magic and you were still the black sheep somehow. The old petulant jealousy clouded your mind until you couldn't think. You had to leave so you could fill your head with something more productive than anger.

For two years you travelled across the country, apprenticing under feldshers and shamans, and even taking a couple of university classes in Irkustsk. The ability to create cures greater than nature's own excited you, and funnily enough, modern medicine returned your love better than mysticism ever did. You even impressed a chemistry professor enough that she asked you to be an assistant in her lab. You worked there for a month. You escaped your family at least partly because you bristled at the idea of being your \cRebel{\sibling}'s lapdog. Without credentials, you would remain a lapdog at the university. That wouldn't do. You had a duty and an inheritance waiting for you at home, regardless of what \cElder{\Parent} thought.

Your homecoming was unsurprisingly frustrating. \cRebel{} still hadn't forgiven you for walking out on \cRebel{\them}. Without anyone else to trust, \cRebel{\they} soon fell in with some big-headed new city doctor. \cOutsider{} is every single credentials-obsessed, intellectually insecure pissant you had to deal with in Irkustsk. Still, you wouldn't have minded the relationship too much if \cRebel{} acted \cRebel{\their} age and knew \cRebel{\their} duties. Instead, \cRebel{\they} spends day and night with the outsider doctor, blissfully unaware that the doctor is using \cRebel{\them} to pry at your family's secrets. That was the entire reason the doctor came to your town. \cOutsider{\They} had been asking around town about your \cElder{\parent} and your family's magic from the beginning. Did \cRebel{} not notice that? Was \cRebel{\they} so besotted that \cRebel{\they} couldn't see past such simple, obvious manipulation?

You worry about \cRebel{} too much nowadays. You've tried talking to \cRebel{\them}, and when reason failed, you threatened to kill that manipulative little doctor in frustration. \cRebel{} still hasn't forgiven you for that. \cRebel{\They} is still cold towards you, even when faced with more pressing issues than your old grudges or \cRebel{\their} ill-advised romance.

Ah, yes, the pressing issues. The plague. You're not sure where it came from. It's unlike anything you've ever studied in the two years you've been away from town. You suspect it is a hemorrhagic fever caused by an errant earth spirit. \cElder{\Parent} has always been reluctant to offer sacrifices to the earth, and you admire \cElder{\them} for that. You've heard that \cElder{\they} eradicated an age-old barbaric tradition of human sacrifice by binding the earth's energy somehow. \cRebel{} thinks it's slavery, but that just makes you roll your eyes. What's the comfort of some vague earth creature next to human lives? You've never heard those spirits they talk so often about anyways. As far as you're concerned, they're units of energy, like heat. You don't worry about the plight of your radiator. 

The metaphorical radiator is malfunctioning now, and you'll have to fix it. \cElder{\Parent} seems to have lost control of the earth somehow and is either unwilling or unable to regain it. You're not the one to take any joy in the deaths of thousands, but you have to admit it presents an opportunity to prove yourself. You're still somewhat bitter that \cElder{\Parent} refuses to trust you with \cElder{\their} secrets, preferring to spout off some excuse about sacrifices and burden. You never understood what that was about. You don't want to marry--you never loved anyone with the kind of raging passion that \cRebel{} is capable of--and \cElder{\Parent} already has a way of making miracles without appeasing the hungry earth. So what was the problem? You could only conclude that \cElder{\Parent} is embarrassed of you. You were born unworthy and you are still unworthy in your \cElder{\parent}'s eyes.

Yet you're the only responsible one in the family anyway. You don't know why \cOutsider{} wanted to use your home as a shelter instead of something smaller but secluded like the Sidorovs' dacha. You thought your \cElder{\parent} made a mistake in agreeing and you were right. \cRebel{}'s research notes and blood-generating Crucible are nowhere to be seen. \cElder{\Parent} is too busy posturing in front of the refugees and \cRebel{} is too busy moping. Only you worry about finding the forbidden research that might spell your family's doom if it ever reaches your enemies. Such is life. At least they're not \textit{asking} you to clean up their mess. That would have driven you mad.

Of course, you will still try your best to protect your family and the unreliable sods that it consists of. You will recapture the earth and contain the plague. You will save the town. Birthright and gifts are nothing next to hard work and intellect, and your family will see that soon enough.

\begin{itemz}[Goals]
	\item Stop the plague
	\item Recapture the escaped earth spirit before your \cElder{\parent} does
	\item Find out how the earth spirit broke free in the first place
	\item Protect \cRebel{}, especially from that manipulative, snake-eyed doctor. Idiot or not, \cRebel{} is still family.
	\item Keep your family's magical secrets from being revealed to the outside world
	\item Be named as your \cElder{\parent}'s successor
\end{itemz}

\begin{itemz}[Notes]
	\item You have very low tolerance for alcohol. Drinking booze will cause you to lose 1 CR for half an hour. The effect is stackable.
\end{itemz}

\begin{contacts}
	\contact{\cElder{}} Your \cElder{\parent}. A tough \cElder{\human} to please.
	\contact{\cRebel{}} Your feckless \cRebel{\sibling}. You do love \cRebel{\them}, though \cRebel{\they} makes it very difficult at times
	\contact{\cOutsider{}} The snake who has your \cRebel{\sibling} wrapped around \cOutsider{\their} little finger 
	\contact{\cCon{}} A childhood friend of yours. You're glad to see \cCon{\them} alive, but you wonder what has become of \cCon{\them} since you left  
\end{contacts}

\end{document}
