\documentclass[char]{guildcamp4}
\begin{document}
\name{\cCbad{}}

You were born into a militaristic warrior caste. Your bloodline has fought wars for the Frith for as long as anyone can remember. After maturation and basic training, you and your clutchmates were shipped to the outer border worlds, expecting to fight pitched battles against alien insurgents and win glorious victories for the Frith. Instead, you found only a backwater planet, far from the action, with a decade-long tour of duty stretching before you and nothing to do to pass the time. Well, almost nothing: as you soon learned from the corrupt local authorities, patrolling remote border space in military warships carries the potential for certain ``fringe benefits." Smugglers, and even legitimate traders, will gladly share a portion of their profits with you, in order to guarantee safe passage of their cargo freighters through uncivilized space. You learned that subtlety and veiled threats--delicate phrasing, knowing how to ask for something without \textit{really} asking--can work to the mutual benefit of all those involved, especially yourself. Just as importantly, it was a way to stave off boredom and add excitement to an otherwise dull and monotonous ten years.

By the end of your tour of duty, the Frith had shifted their foreign policy from aggressive expansion to gradual colonization of uninhabited space and peaceful negotiation with immediate neighbors. Much of the Frith military was decommissioned, and you found yourself reassigned as a domestic police officer, responsible for patrolling the Human-Ver region of Frith space. Fortunately, you were partnered with one of your clutchmates and fellow infantrymen, and the two of you gradually resumed ``taxing" the local trade, just as you had when stationed on the frontier. However, the local authorities proved to be less accommodating this time around, and your partner was eventually indicted on charges of bribery and extortion. Fortunately for you, your clutchmate shifted all of the blame onto himself to avoid implicating you, and for this you owe him a debt of gratitude that you are trying to find a way to repay. Less fortunately, you have begun receiving anonymous messages claiming that someone ``knows about your activities on the frontier", and that unless you find a way to pay them an exorbitant sum of credits, you will soon join your clutchmate in prison.

On top of all of this, your new partner \cCgood{} has proven to be a stickler for the rules, as well as an insufferable, idealistic greenhorn. You've lost count of the number of times \cCgood{\they}'s mentioned that \cCgood{\they} descends from a long line of honorable police officers, the heroic escapades of this-or-that great-great-grandfather, and how \cCgood{\they} scored the highest out of \cCgood{\their} clutch in the Academy. Just the other day, \cCgood{\they} enthusiastically went on about how \cCgood{\they} couldn't \textit{wait} to promote out of border patrol and make detective. Obviously, you've had to put your tax collection duties on hold, since the slightest whiff of illicit activity is sure to immediately make its way into an Internal Affairs report, courtesy of Officer Boy Scout. Even worse, your plan to save up enough credits to pay off the anonymous skeleton in your closet is now seriously in jeopardy.

Today, you have an off-the-books rendezvous scheduled with \textit{TIS Chivalry}, a Veran ship that you've had smooth dealings with in the past. This should net you a tidy sum, once you perform your cursory inspection, stamp their papers, and send them on their way. However, you have an unexpected guest aboard: \cPilot{}, a parolee who was assigned to your ship just this morning as part of an ex-con reintegration program. Apparently, the powers-that-be have decided that \cPilot{}'s piloting and navigation skills would be of use to law enforcement, and today is your turn. In addition, the overeager Officer \cCgood{} has thrown a second monkey wrench into your plans by somehow noticing \textit{TIS Chivalry} on long-range scanners several hours earlier than agreed upon. \cCgood{\They} even hailed the \textit{Chivalry} and commenced docking procedures, which should finish in about 15-20 minutes. You sincerely hope that the Ver have enough time to make everything look kosher and ship-shape by the time \cCgood{} gets aboard and starts sniffing around.

But first things first. Protocol dictates that all foreign contact needs to be reported to HQ, and the \emph{Anodyne}'s transmitter has been on the fritz, so you need to get \cCgood{} and \cCbad{}'s help to send a transmission to HQ before docking finishes.

\begin{itemz}[Goals]
	\item Work with \cCgood{} and \cPilot{} to report your situation to Border Patrol HQ before docking completes.
	\item Ask \cVone{} about the bribe they promised you, in private.
	\item Make sure TIS Chivalry passes inspection.
	\item Ensure that TIS Chivalry reaches Ver space.
	\item Prevent \cCgood{} from observing illegal activity. Failing that, prevent \cCgood{\them} from uploading \cCgood{\their} findings to the ship's black box.
	\item Actively mentor \cCgood{} by providing advice and assistance.
	\item Make sure \cPilot{} doesn't violate \cPilot{his} parole. 
	\item Cover up your history of corruption.
	\item Pay off whoever is blackmailing you.
	\item Help your imprisoned clutchmate any way you can.
\end{itemz}

\begin{itemz}[Notes]
	\item You have a login and password for the computer terminal on the \emph{Anodyne}.
	\item You know the code for the locked compartment on the \emph{Anodyne}.
\end{itemz}

\begin{contacts}
	%\contact{\cTest{}} <- This is the format for contacts 
	\contact{\cCgood{}}
	\contact{\cPilot{}}
	\contact{\cVone{}}
\end{contacts}

\end{document}
