\documentclass[char]{Pestilence}
\begin{document}
\name{\cCon{}}

So this is what the end of the world looks like.

They'd call you a fraud, a snake, and a murderer, but you are simply a nihilist. The plague has destroyed half the town in a week. You've seen the blood and pus oozing from every inch of their bodies. You've seen their pink eyes, swollen tongues and twisted joints. It's a divine punishment, not a challenge despite what those other doctors seem to think. Doesn't mean you specifically have to get punished. Oh, on the contrary, you're getting rich. You can't be hurting anyone by selling them hope, especially when there is little real hope.

You've always thought the town's elders to be frauds. Even the elder's \cApprentice{\offspring} couldn't explain to you how on Earth all this magic worked. The recent plague makes you wonder if there truly is some special force in the universe, but it's too late for soul-searching now. You grew up in a town of frauds, saw it profitable and decided to make your living as a fraud. It has been working quite well until recently. You have your own little pharmaceutical industry now. The townsfolk eat up your special cures without questions. Some even report feeling better; placebo is the biggest cure, after all. Your distributors are trustworthy. Your pyramid is so tall no one could hope to find you at the top.

That was until the big city doctor traipsed into town. You don't know what \cOutsider{\their} original deal was, but \cOutsider{\they} decided to poke \cOutsider{\their} snooty little nose into your business anyway. You have a bit of fondness for the townsfolk; you had grown up with many of them and some even offered you shelter when you were struggling. But this pretentious little shit gallivanting around town thinking \cOutsider{\they} knows everything...you would have wanted to kill \cOutsider{\them} even if \cOutsider{\they} hadn't started interfering with your business. The rumor that \cOutsider{\they} could notify the authorities and bring in law enforcement from outside was the very last straw.

You paid the doctor a visit a week ago with your trusty revolver. Poor naive \cOutsider{\human} didn't think twice about opening the door to a stranger in the middle of the night. You shot \cOutsider{\them} before \cOutsider{\they} could see past your bandana. You expected the act to be quick and painless, but the shock of it paralyzed you for a good second. You hadn't exactly spent your whole life killing people. In your panic, you didn't check if the job had been done properly. That might have been your biggest mistake.

To be fair, you didn't expect the doctor to survive. You were quite sure you shot \cOutsider{\them} in the heart. The blood on the floor could have filled a bucket by the time you managed to find your legs. Yet, there \cOutsider{\they} was, barking orders and being \cOutsider{\their} usual pompous self in the shelter. You wouldn't have been too surprised if \cOutsider{\they} was bedridden or at least a little bit paler than usual. It was a tough night; perhaps you overrated your aim or misremembered the amount of blood. But no amount of human healing could bring the doctor so quickly from death's door.

The situation is inconvenient to say the least. The doctor thankfully seems too focused on the plague to look deeper into your pharmaceutical empire, but earth only knows what \cOutsider{\they} is going to tell the army when it comes for all of you. Not to mention how \cOutsider{\they} might affect your new lucrative new business model...

Like any good dealer, you have eyes and ears everywhere. One set of eyes and ears brought to your attention a potion concocted by a desperate plague victim, consisting of herbs, crushed pills and who knows what else. The man consumed his potion, and miraculously enough, he survived and arrived at the shelter. Only the uninfected could enter the shelter, so whatever he made had worked--well enough to fool the doctors, at least. Unfortunately, by the time you found him, he was too delirious from pain to give you any answers about what he made. Either the plague, the potion or both had wreaked havoc upon his body, and he died soon afterwards. 

It wasn't a total loss, however. You managed to procure two doses of this mysterious potion from the man's body. One dose might be good for testing--not on yourself, of course, there's nothing in the world you trust so much. If the test works, the other can be given to a talented chemist to be replicated. If your partner is profit-minded, it could be the start of a beautiful friendship. If not, well, more profit for you.

\begin{itemz}[Goals]
	\item Get out of town alive
	\item Sell your cures and make as much money as possible
	\item Prevent your business from being exposed
	\item Find out what foiled your assassination attempt last week
\end{itemz}

\begin{itemz}[Notes]
	\item Item 0012 is the only potion you have that might have curative properties. The rest are your typical ware
\end{itemz}

\begin{contacts}
	\contact{\cOutsider{}} A nosy \cOutsider{\human} who may need to be silenced. However, you're not keen on acting rashly until you're sure \cOutsider{\they} won't crawl out of the grave again. And \cOutsider{\they} does seem to know \cOutsider{\their} chemistry...
	\contact{\cApprentice{}} An old friend of yours before you were pulled to your respective careers. Has a surprisingly big brain on those stubborn shoulders. You wonder if the big brain holds any knowledge you may need.
\end{contacts}

\end{document}