\documentclass[char]{guildcamp4}
\begin{document}
\name{\cJames{}}

\bigquote{``Immortality is not a gift, Immortality is an achievement; And only those who strive mightily shall possess it."}{- Edgar Lee Masters}

You are old, much older than what most men ever live to see. Not as old as your fellows aboard this ship, though you appear the oldest of the lot. That makes you feel a bit bitter, but at least you have your near-immortality. Some men say that they would not like to live forever. Of course they would say that, given that they'd never been able to get close enough to taste immortality. They have to rationalize to accept their short, brutal lives. But you... you have tasted it, and the taste was blood.

Of course, you did not always have knowledge of immortality, and focused your attention on more mundane pursuits. You were born in a simpler time in London, England, in the year 1791. Your father owned a small company, and your mother kept the home. You did your early studies under your uncle and a Reverend. Quickly you became fascinated with the field of medicine, of the workings of the body, the circulation of the blood, of reproduction, new life replacing old. You saw suffering all around you, and medicine was a way to reduce that suffering and extend the life. However, death still came. During your early studies, you realized that this reality disturbed you much more than you had expected. It was this reason, combined with your fascination with the physiology of the female body and reproductive system, that led you to the field of obstetrics. Though woman and child could die during pregnancy and childbirth, the focus of your work was on bringing new life into the world, rather than focusing on the death and decline of the body.

You got your MD in 1813, after which you began to lecture on physiology and midwifery, and eventually taught on the field of obstetrics and diseases of the female body. Your lectures saw large numbers attend, and you gained a respected position at your hospital. By 1818 you began your life's work, regarding the transfusion of blood from one human to another to treat a variety of ails. You had been witness to the death of many during childbirth, which you found very upsetting, and proposed that blood could be taken from one person and used to treat severe postpartum hemorrhaging, preventing the patient from bleeding out. You experimented on animal test subjects to determine whether such a treatment would be possible for humans. In doing so you learned the techniques and precautions necessary for a successful transfusion of blood. In 1829 you finally performed your first successful human-to-human blood transfusion, and it would not be your last. You were able to get your results published in prestigious journals and later went on to invent a variety of instruments for use in the transfusion of blood.

You eventually left the first hospital you taught at, becoming a fellow of the Royal College of Physicians in 1838. You also had a private practice that left you quite rich. You were quite comfortable, though you never found love, instead living with your grand niece, though you owned two homes. It was less lonely that way. You retired in 1847, though you still occasionally saw some patients after that, though not at "normal" hours, after which you spent much of your leisure time reading books. You would never leave the house without a book. They were your constant companions, your escape from the ever-present awareness that you were aging, death slowly creeping up on you.

Sometimes you wonder why the Ver didn't take you earlier, back when you were in your prime. But no, it took them until 1879, when you were a very old man, for them to break into your room in the middle of the night and snatch you away to their ship. Later you learned that they left a sort of copy behind, a body that looked just like you, but with no life in it, to divert the suspicions of your family. But then all you understood was that a figure appeared in your room, grabbed you around the waist, and then you lost consciousness. You woke up aboard TIS Chivalry, a vessel that travels through the stars rather than the sea, captained by a race most alien, known as the Ver. The Ver named \cVone{} stood before you, smiling. \cVone{\They} held up a glass of dark red liquid to your mouth and made you drink it down. At first you almost gagged, realizing that it held blood, but then something remarkable happened. The taste and consistency became pleasant, and by the time you drank the last drop you had taken the glass from \cVone{\their} hands and tipped it back yourself.

Almost instantly you felt a surge of... vibrancy--yes, that is the word--run through your entire body. In your later years you had become quite feeble, but after drinking \cVone{}'s blood you felt decades younger. However, your body did not change. You had more energy and felt strength return to your arms and legs, comparable to that which had been present in your middle age, but you would never look young again. It was quite strange to be able to feel that way again, yet see the same old man in the mirror.

After your initial burst of shock and joy, you were faced with the truth of your new reality. Drinking that blood bound you to \cVone{}, turning you into what is known as a ghoul. You would be able to continue on nearly indefinitely without aging further, without becoming more feeble, but you would have to continue regularly consuming the blood of the Ver. And there was a catch. The one who had captured you had claimed you as \cVone{\their} slave, and you would have to use your new strength to serve as crew aboard TIS Chivalry. And so serve you have, for centuries. The world you left behind is long gone, and your new reality has since become monotonous, and even you find yourself numb at times to the monstrous acts you are made to commit for your master.

See, the Ver regularly kidnap humans from Earth and sell them into slavery, and as a crew member, you are tasked with helping to subdue and transport these humans to market, betraying your own race. At first you refused to do it, but you quickly learned that if you were to do so that \cVone{} would withhold \cVone{\their} blood from you, after which you would regain your weakness and begin to age again. After the first time you came crawling back to \cVone{}, begging for forgiveness. \cVone{} only laughed as \cVone{\they} drained \cVone{\their} blood into a glass for you, which you drank greedily, regaining your strength. You never refused again.

As long as you complied with \cVone{} and the other officers aboard the ship, \cVone{} granted you the privilege to continue some of your experiments and inventions, ultimately for \cVone{\their} amusement. That was why \cVone{\they} took you in the first place, because your work with blood amused \cVone{\them}, and so you would continue to be a source of amusement to \cVone{\them}. Of course, over the years you knew that medical science must be advancing on Earth, and only rarely would you receive a glimpse of it, or some new kind of tool to work with. On the other hand \cVthree{}, the Ver Medical Officer, always has the most advanced alien scientific equipment. You envy \cVthree{\them} strongly. Your work is never truly appreciated. You are nothing but a plaything to \cVone{}.

And you were not the only enslaved human crew member of TIS Chivalry. There were other ghouls who came before you, and another who came after you. The oldest of all of you is \cJoan{}, the actual Joan of Arc, plucked from the stake as she burned. You envy her appearance of youth. After all these years, she still appears no older than 20. \cJoan{} has always been polite and courteous towards you, though overly preachy at times, disapproving of your study of the body and blood in particular. You lost the faith of your parents long ago, but ever she clings to her belief in God, though she also believes that she is in Hell. You certainly don't blame her for it. And then there is \cJulie{}, who was a French opera star during her time on Earth, about a hundred years your senior. Though she is much older than you, she still acts like a youth, always on the lookout for adventure and romance. Some might even go so far as to call her crass, uncouth, and unchaste, acting more like a man than a lady. There is something a bit off-putting about her. Perhaps it is the fact that she seems so unaffected by her life as a slave aboard the ship, and even seems to enjoy it. But perhaps this is just because she's had more time to get used to her life here, or because she's stronger on the inside. Either way, she seems to be much happier than you generally are.

Then there is \cRasputin{} a Russian holy man who arrived a few decades after you. Quickly you realized that he seemed to know more about the Ver than he let on. Curious about your experiments with blood, he found it in himself to reveal a secret to you that he had kept to himself his entire life, and must continue to keep from the rest of the Ver if he wishes to continue to live. \cRasputin{} is a hybrid creature, with a human mother and a Ver father. In the years since you became a slave, you had learned that such creatures were generally despised by the Veran populace, and specifically despised by \cVthree{}, who regularly called for their deaths. Taking pity on him, you developed a serum for him to take that would disguise his hybrid nature if his blood were to be sampled by \cVthree{} or some other Ver. You know that \cVthree{} is trying out some new test on everyone onboard, and that his serum is wearing off, so you need to produce a new treatment before \cVthree{} can get to him and demand his blood. Unfortunately, you have recently dealt with some broken equipment, so you can only formulate the serum if you are to get equipment elsewhere. The only place you know you can get such equipment is in \cVthree{}'s lab.

You have also been working in secret for years on creating a substitute for Veran blood, which would make it possible for you to escape captivity and continue to live without aging, without bondage, without frailty. You are on the verge of a breakthrough, but once again, you need equipment, and soon. Now seems the ideal time to finish your research, given that this raid has been nothing but trouble for the Ver. They lost their Intelligence Officer to a mob of humans, and they have been having trouble with putting the captured humans into the stasis pods. They have also picked up a new pet for \cVone{}, who is not cooperating. On top of all that, it turns out you may have some trouble passing through the territory of the Frith, a race of alien police who strictly patrol their borders, but generally do not post a problem to the Ver. In all the confusion it may be possible to sneak into \cVthree{}'s lab and steal the parts you need to fix your equipment.

Perhaps you can even do more than finish the blood substitute. With that technology, it may be possible for you to find a way to return to Earth. You know that most of the ships systems are controlled by the blood of the user, in such a way that the identity of the user can be verified. But \cVone{} has a ring that allows the wearer to bypass such security. If you were to get ahold of this ring, you would be able to control one of the shuttle pods and take it back to Earth. You yearn to see what the world of the future is like, and to learn its advanced medical knowledge and technology. All these years you've been kept from it, being teased with mere glimpses. 

But before you even try to leave, there are a few other things you want to get done. You've heard talk that \cVone{}'s new recruit is a scientist who studies the blood, much like you, but from a world much more advanced than the one that produced you. If you were to return to Earth with the knowledge you have you would be like a fish out of water, unable to make your way in a futuristic world with a 19th century mind. No, first you will have to acquire some sort of research either from the new scientist or from \cVthree{}. That way you can develop it further and make money from your work on Earth, allowing you to live comfortably once again.

Also, if in fact the Frith board TIS Chivalry, you may be able to get their help. You know that their laws forbid slavery, so if you were to present them with your plight, perhaps they would help you and your fellow humans escape to Earth. But you must be careful in how you approach them. If the Ver catch wind of you trying to sabotage their cargo and betray them to the Frith, they will surely kill you. The Ver are inhumanly powerful, and not to be messed with. Even the Frith are no match for the Ver.

If at all possible during your attempts at escape, you also wish to free as many humans as you can, particularly those that can share knowledge with you about the Earth of today. You especially want to talk with the new scientist, who is currently being held in a locked room with the human who cannot be put into stasis. They both may prove helpful to your efforts.

Today may be your only chance to escape the Ver, and to help others to do the same as a means of atoning for all the sins you have committed at the orders of the Ver. You are not a religious man, but you feel the need to seek forgiveness. So you'd better get moving and make this last chance count.

\begin{itemz}[Goals]
	\item Steal enough of \cVthree{}'s equipment to repair yours.
	\item Make and deliver the serum for \cRasputin{} before \cVthree{} tries to test his blood.
	\item Finish developing artificial Ver blood so you can survive away from the Ver and remain near-immortal.
	\item Steal \cVone{}'s ring and use it to escape to Earth.
	\item Acquire research and knowledge of Earth from humans or \cVthree{}.
	\item If possible, alert the Frith to the illegal slaves aboard TIS Chivalry without endangering yourself or others.
	\item Free as many humans as you can.
\end{itemz}

\begin{itemz}[Notes]
	\item It has also been a while since you've had Ver blood, so you will want to acquire and drink some by t + 2 hours. Your artificial Ver blood will count towards this.
\end{itemz}

\begin{contacts}
	\contact{\cVone{}} - The Ver who owns and commands you. You require the blood of his kind to survive. You obey him, but on the inside you hate him and all his deeds. You wish to relieve him of his control ring to allow you to pilot a shuttle pod.
	\contact{\cVtwo{}} - The Engineering officer aboard TIS Chivalry, a particularly nasty Ver.
	\contact{\cVthree{}} - The Medical officer aboard TIS Chivalry. \cVthree{\They} hate hybrids and poses a threat to your friend \cRasputin{}. You envy \cVthree{\their} equipment and will need to steal some of it to advance your goals.
	\contact{\cRasputin{}} - Another ghoul and the closet thing you have to a friend. You provide him with the serum that allows him to hide his mixed nature from the Ver. 
	\contact{\cJoan{}} - A ghoul aboard the ship. She is nice enough, though she strongly disapproves of your science.  
	\contact{\cJulie{}} - A ghoul aboard the ship. Kind to you, though raucous and rough around others. Seems to enjoy her captivity a bit too much. 
\end{contacts}

\end{document}

