\documentclass[char]{guildcamp4}
\begin{document}
\name{\cJoan{}}

\bigquote{``If I am not, may God put me there; and if I am, may God so keep me. I should be the saddest creature in the world if I knew I were not in His grace.''}{}

{\bf Note: You are schizophrenic, and the visions you see are hallucinations. However, you are not aware of this and will not ever be convinced that your visions are not real. Roleplay accordingly.}

You are in Hell, and the demons they call the Ver are your assigned tormenters. You serve aboard their ship of the dead, called TIS Chivalry out of some sort of cruel irony, forced to aid in the torment of human souls. Most of these others are sent on to somewhere else, to some other demons, but here you stay. The demon called \cVone{} has taken a particular liking to you, keeping you among \cVone{\their} personal slaves. As this is your righteous punishment, you obey \cVone{\their} orders. For the first few decades you spent every day in tears. After a century you settled into a new personality, dark, yet never truly resigned to your fate. How did you end up here, tormented by devils? No matter how many years--centuries--have passed, you still cannot figure out what you did to deserve being damned, denied the sweet presence of the Lord. Yet you must have performed some grave sin, or else you would have been left here to rot. You look back over your life, searching again for an explanation.

You were born in the village of Domr\'{e}my in the year of the Lord 1412, in a part of France still loyal to the crown. You grew up surrounded by war. There were many raids by the Burgundians on your village, which was once even burned. All of this during your childhood. At the age of 13, you began to be visited by visions of Saint Michael the Archangel, Saint Catherine, and Saint Margaret. They were beautiful, so beautiful that you cried. They told you that it was your destiny to drive out the English and deliver the Dauphin to Reims to be crowned king. 

At the age of 16 you were able to gain an audience with the French royal court. Despite much scoffing, you proved them all wrong when you delivered a prediction of a French defeat. After that they took you seriously. You told them that you must be at the King's side, that there would be no help for the French if not through you. It was the will of God, as the saints delivered to you.

It so pleased you to do the will of the Lord, and you did everything you were told. Through your words you turned the ongoing war with the English into a holy war. Some suspected you to be a sorceress or some other kind of sinner, but when the Dauphin ordered inquiries into your theological background, they declared you to be "of irreproachable life, a good Christian, possessed of the virtues of humility, honesty, and simplicity." The Dauphin finally believed that your mission was one given by God.

You were given a place among the hardened military men, your mouth speaking forth holy advice to those decades your elders. You even walked into battle, holding your banner high. You never directly killed anyone, but your words and actions led to the righteous deaths of many of the enemy. While at the right hand of the French military commanders, the army enjoyed what those of little faith would call almost unbelievable success. Your presence and advice, blessed by God, was able to turn the tide of the siege of Orl\'{e}ans.

You remained with the French army through several other campaigns, surviving several wounds to your body. Yet the rough conditions could not wound your soul. You followed the army through many successes and some failures, but you never faltered in your faith. But your influence could not last.

In May of 1430 you were captured by the Burgundians, allies of the English. They imprisoned you in a 70 foot tower, from which you jumped in an attempt to escape. After that the Burgundians moved you to a different place of imprisonment, after which you were transferred to English custody. Your captors talked at you with spite, telling you of the failed attempts to rescue you. Yet still you did not despair. You turned your eyes towards God, confident that you would survive to continue aiding the French in defeating the English. But you were wrong.

They tried you for heresy. Heresy! And with a tribunal filled entirely with English and Burgundians. At every step those who brought you to trial sinned before God. They had no true evidence of heresy against you, yet brought you up on trial anyway, denying you the required impartial tribunal. At every attempt they made to entrap you into admitting heresy, you were able to evade them. After all, your intentions were pure and your actions came from the Lord. They even accused you of cross-dressing for donning garments that were necessary to protect your body and purity. Many theologians defended your actions. Yet still they condemned you to die. Perhaps you had a sinful thought, or blamed God for forsaking you rather than accepting your position as a martyr. Perhaps that was your sin. But after all these centuries you cannot remember your thoughts then. Except for the fear. Perhaps that was it. You asked that someone hold a crucifix before you as you died. This small concession was granted to you. Then they burned you alive. You remember the pain and the stench of burning flesh, and then blackness.

You woke up in Hell. The demon called \cVone{} held your head and poured a glass of what \cVone{\they} said was \cVone{\their} blood down your burned throat. Shamefully, you gulped it down. It eased the burning and tasted so... good. That sealed you to \cVone{\them}. Over time your wounds healed, but you were bound to serve \cVone{\them} and drink the blood of the Ver, a prospect which hurt you even more than the burns. Over the centuries you almost came to accept that this was God's righteous punishment, and that you deserved to serve as a slave of demons. The saints had abandoned you, and you were tormented by visions of the Devil and his angels. So passed the years, with dark visions and servitude. 

But... after hundreds of years of silence, the image of Saint Michael appeared to you again. You wept at the sight of his sweet face, and he sheltered you in his wings. It was over almost as soon as it had begun, but his image lingered in your mind. Would the saint visit one of the damned? No, he would not. So could you perhaps be in Purgatory, being cleansed of your sins in preparation for Heaven? Or was the image yet another torment only intended to make you desire the sweetness of Heaven even more, though you could never reach it? At the very least, there is a chance that you may still be able to attain it. If you are truly in Purgatory, it is up to you to do all you can to cleanse yourself and your fellow sufferers of sin and reach for Heaven. 

You find that your demeanor changes almost overnight. You feel the return of something that you have not felt in centuries: righteous fervor. You try to convince the others bound to \cVone{} that they may yet have a chance for redemption and to improve their sinful ways, but most of them simply laugh at you, calling you insane. Yet it is them who are insane. Somehow they believe themselves still alive, though no one here ages like a living person. Still you feel it is your duty to guide them towards the Lord. The stink of their sins torments you. Whenever you see them commit evil acts, chastise them and point them in the correct direction. \cRasputin{}, another soul bound to \cVone{}, strikes you as a heretic. He keeps to himself about his beliefs, but you know he was a follower of a heretical sect in life and have heard whispers that he dabbled in the dark arts. Keep an eye on him in particular. 

As for \cJulie{}, you know that she enjoys violence for the sake of violence and revels in material comforts. On the other hand, she has an unusual demeanor around you that you cannot quite read, but she certainly seems overly fond of you. Almost too fond. She is always kind to you, never coarse like she is around the men. For this reason you have some fondness towards her, despite her sins. It is because of your fondness for her that you try to direct her towards righteousness.

Some of their actions seem particularly heinous. You know that some of those you call demon and some of your fellow souls, called ghouls, dabble in some sort of blood magic. Some call it science, but you know that anyone who drains the life force from a body is committing an evil act. \cJames{} may appear as a kindly old man, though in fact he is far younger than you, but he does ghastly things with blood in the name of "science." Do all you can to prevent such evil undertakings, for this is the righteous path. As for yourself, do not submit to blood "science." You know the Ver called \cVthree{} desires the blood of you and your fellow humans for some monstrous act. Do not allow him to take it and use it in some arcane rite. It is enough that that they feed upon you and your fellow souls for their sustenance.

In regards to your own actions, do what is righteous in your understanding, and avoid all sin and appearance of sin. If you ever receive a holy vision again, you are to follow what the Lord passes on to you to the letter. Failing to do so will be taken as a sin in the eyes of the Lord, and could cause you to falter in your faith.

Above all, make it your primary goal to discover whether you have a chance of salvation. You want to find out whether you are in Hell, permanently damned, in which case you are to accept your righteous punishment and obey your demonic masters, or in Purgatory, being cleansed for Heaven, in which case you must do all you can to reach redemption, aid those around you in attaining Heaven and rebuke all evil. You are certain that if the latter is true, God will show you the way to redeem yourself and others. You feel like you are so close. You have served so many centuries aboard this ship of blood. You desire so greatly to see the sweet face of Jesus that has been denied to you all these years.

One bit of information that has stuck with you over the years is the knowledge that you are capable of creating a sort of "holy water", though it may be blasphemous to call it such. You learned that if you pray sincerely over a vessel of water, it becomes like acid to the skin of the Ver. At times they have called upon you to create such water for use against other Ver, and you have accepted this as a part of your torment, being forced to give something holy up to evil use. Accepting your place, you have never used your gift against the Ver who hold you captive. But if this were truly, undeniably Purgatory... It would certainly be satisfying to use it to punish doers of evil, as doing so would be God's will. Somehow though you feel less enmity towards \cVone{}, the one who fed you \cVone{\their} blood and made you \cVone{\their} ghoul. \cVone{\They} does not torture you, but treat you more like a pet. You are conflicted by your feelings towards \cVone{\them}. If it came down to a time where you were once again commanded to destroy evil, and this evil was \cVone{\them}, would you be able to do so? You are not sure, and this makes you feel ashamed. You do know though that \cVone{} has a ring that allows \cVone{\them} or anyone who wears it to control the ship. You are sure that this information would be helpful in the case that you are tasked with destroying \cVone{\their} influence over the humans aboard the ship. It would also allow you to do this without violence.

On this particular voyage through the void between worlds, you have helped to restrain and put to sleep hundreds of new human souls, which TIS Chivalry is ferrying to their place of torment, the homeland of the Ver. But you hear worry in the voices of your masters. Something is wrong. Not only did they lose one of their own during the process of obtaining human souls, the on they called the "Intelligence Officer", you know from years of experience that you have to pass through the territory of the beings called the Frith, who seem to hold some power over the Ver in their territory. The Frith do not allow the ferrying of human souls through their territory, and \cVthree{} is having trouble putting one of them to sleep in the hold of the ship, so this new one cannot be hidden away from the Frith. There is also a new potential ghoul on the ship who is not resigning to their new fate. If this is Hell, your duty is to help your masters to deal with the situation. But if this is Purgatory, is it not your duty to do all you can to bring these new souls to God? In that case, the means by which you bring them to God would be up to Him, as worked through you.

But first you must determine where you truly are. Ideally, you hope you can do so before the Frith reach the Veran vessel, so you can know who you are to help. But if you do not manage this, you suppose that you will assume that you are in Hell, as you have for the past centuries. You cannot be certain that you are in Purgatory based on one vision alone. Follow your sense of what is good and holy and surely you will receive your answer.

\begin{itemz}[Goals]
	\item Determine whether you are in Hell or Purgatory.
	\item If you believe you are in Purgatory, do all you can to redeem yourself and others in God's eyes and thwart all evil you encounter.
	\item If you believe you are in Purgatory, try to bring the newly caught human souls to the Lord.
	\item If you believe you are in Hell, do all you can to accept your fate and do the bidding of your demonic tormenters.
	\item If you believe you are in Hell, help your masters ensure that the inspection goes in their favor.
	\item Do all you can to prevent the evils of blood "science" or magic aboard TIS Chivalry and do not allow anyone to take your blood.
	\item Chastise your fellow humans if you see them perform any evil act.
	\item Avoid all sin or appearance of sin.
\end{itemz}

\begin{itemz}[Notes]
	\item It has been a while since you have consumed the blood of the Ver demons. You know that you become weaker if you do not drink it. You sense that some of your strength will wear off if you do not have more by t + 2 hours.
\end{itemz}

\begin{contacts}
	\contact{\cVone{}} - The Ver demon who owns and commands you. You are ashamed that you feel some sort of fondness towards \cVone{\them}.
	\contact{\cVtwo{}} - An officer of mechanical science aboard TIS Chivalry, another Ver. You feel a general sense of disgust toward \cVtwo{\them}, as you do towards most of the Ver.
	\contact{\cVthree{}} - The medical officer aboard TIS Chivalry. \cVthree{\They} engage in blood "science", which repulses you. You want to avoid letting \cVthree{\them} take your blood and to prevent \cVthree{\them} from advancing \cVthree{\their} heinous work.
	\contact{\cJames{}} - A ghoul aboard the ship and worker in blood "science". You do not want to allow him to take your blood and desire to thwart his work. However, he is kind to you, so you wish him no harm and have no strong feelings of enmity towards him, though his work repulses you. Perhaps he can be redeemed.
	\contact{\cRasputin{}} - A ghoul aboard the ship. A heretic rumored to be involved with the dark arts. Keep an eye on him.  
	\contact{\cJulie{}} - Another ghoul aboard the ship. She is kind to you, so you feel fondly towards her, despite her sins. 
\end{contacts}

%mem packet regarding love letter

\end{document}

