\documentclass[char]{guildcamp4}
\begin{document}
\name{\cJulie{}}

\bigquote{``I think the older I get, the more I realize that the ultimate luxury is time.''}{- Michael Kors}

You enjoy the finer things in life, and have gotten good over the course of the centuries you have been alive at getting them for yourself, whether through your wiles or at the end of a weapon. Of course, this whole enslavement thing has kept you from your ideal, but it certainly has its perks. Unlike some people, you know how to make the most of a situation to bend it towards favoring you. You grab life by the balls and make it beg for mercy. The Ver may not know it yet, but you will soon be considered their equal...

But you're getting ahead of yourself. You think of how you got this far, on the verge of immortality and power. You certainly didn't start out low-born, though you were born a mere mortal. A mere mortal born into a life of privilege and opulence in 1673, but a mortal nonetheless. Your father was the Grand Squire of France, which gave your family some measure of prominence among the nobility. His job was to train pages for the king, and he took it upon himself to train you in the same manner. You learned the art of how to use a sword, horseback riding, reading, dancing, how to win in a bare knuckle fight, and other practical skills. You quickly learned to enjoy a good fight, a good drink, a good roll in the sheets, a good night of gambling, and duels in particular. Some called you coarse and unchaste, but never to your face. You gained quite a reputation for protecting your honor with violent force.

At one point you got married off in name only to a titled man by the name of Maupin, who went off to live elsewhere for his job, leaving you behind in Paris. This gave you much more freedom as a "married" woman than most women of your generation. You were able to get away with quite a bit of tomfoolery in your youth. At a young age you met up with a fencing master by the name of S\'{e}rannes, who taught you some new tricks. Eventually you surpassed him in skill. When S\'{e}rannes got in trouble with the law for being involved with an illegal duel, you both fled to Marseille. You made a living giving sword fighting exhibitions in front of audiences, during which you challenged audience members to duels and got to show off your superior skills. These acts were combined with singing, your other strongest talent, which caught the attention of those involved with the Opera. Eventually you became "La Maupin", the most famous actress of your time in the Paris Opera. Of course, you didn't let the Opera rob you of your personality, and you continued to duel for your honor, go on adventures, and romance both men and women. In fact, you would dare to suggest that your love life was improved greatly during your time in the Opera. 

Your ravishing beauty and charm allowed made the men drool and the ladies swoon. Though the mores of your time were disapproving of the kind of romantic behaviors you enjoyed, you still managed to get away with everything, even when society tried to steal them away from you. For example, you once fell in love with a ravishing woman who returned your feelings. Her family caught wind of your relationship and forced her into becoming a nun. Undeterred, you took the vows as well, set the convent afire, and ran off with your lady love in the ensuing confusion. The relationship didn't go on forever, but it was fun and fulfilling while it lasted. You were charged in absentia for your "crimes" and sentenced to death, but you didn't let silly things like that interfere with your fun.

On another occasion a nobleman insulted you for wearing men's clothing. You responded by challenging him to a duel and winning. You didn't think to kill him, just humiliate him, so you checked up on him the next day to ensure you weren't a murderer. He still lived, and you found a spark lit between you and him. The two of you became lovers for a short while, and remained in friendly contact for the rest of your life.

These were far from your only adventure. One time you attended a royal ball dressed as a man, wooing all the young noblewomen. There were some men who weren't very happy about this, but you defeated all of them in a test of swordplay. This was unfortunately illegal, which got you into a bit of trouble, so you spent some time outside of France to avoid legal action. During that time you went on to have an affair with a prince. Eventually you did spend some actual time with your husband, but you remained an actress in the Paris Opera all the while. No man could keep you from fame, fortune, adventure, and luxury.

You didn't stay with him forever, though. During the later years of your mortal life you were in a relationship with a Marquise. She died young, sending you into a dark depression and prompting you to retire from the Opera in 1705. You spent time in a convent to recuperate from your loss, during which time you "died." Of course, that was when things really got interesting.

One night you sat alone on your uncomfortable cot, questioning your direction in life, when a tall, handsome, inhuman-looking being appeared before you, clapped \cVone{\their} hand over your mouth to prevent you from screaming, and then everything went black. You woke up aboard \cVone{\their} ship, the TIS Chivalry, a ship that travels between the stars. \cVone{\They} presented you with a tall glass of what appeared to be wine. Parched, you took a large swig without looking too closely at it, only to discover that it was blood. Shocked, you were unable to protest as \cVone{} gently tipped the cup back, allowing the rest of \cVone{\their} blood to flow down your throat. You would only learn later that this blood was both a gift and a curse. It transformed you into what is known as a ghoul, a human that is dependent on the blood of the alien beings known as the Ver to survive. However, consuming this blood regularly has slowed the process of aging to a bare creep, allowing you to still appear young after centuries.

Becoming a ghoul made you a slave to \cVone{}, which which was rather hard to accept the first few years. At first you tried to rebel, or to escape servitude, only to discover that being denied the sweet nectar of Veran blood for more than a few days left you feeble. It would also allow you to begin aging again, though you were never gone long enough to feel the effects. You always came back to \cVone{}, who found your antics more amusing than concerning. Eventually learned that there were better ways to get what you wanted, and that to comply left you with a great deal of freedom. As long as you stayed in \cVone{}'s favor and allowed \cVone{\them} to feed on your blood, \cVone{\they} would pamper you and give you privileges that you would otherwise not receive. You know that \cVone{} considered you no more than a pet, but you took what you could get, manipulating the situation to your advantage. All you had to give in return for your favor was your blood and your labor aboard the ship, if you could really call it that. Working aboard the Veran ship was like a new adventure. You got to fly about the stars, meet alien races, and stand upon alien planets. Sometimes you were even allowed a sort of shore leave, during which you were able to mingle with the locals and purchase local trinkets and treats with the small amount of money \cVone{} gave you. At first you found the business of trade in humans for their blood distasteful, but eventually you got used to it, readily participating in their capture, keeping, and sale on the Veran homeworld.

All of this has kept you entertained over the years, but gradually even adventure of this sort is beginning to grow old. You tire of the same old routine and being subject to \cVone{}'s whims. You want true freedom, and to regain a sense of power over your life. It took you years of sneakily listening in on private conversations and asking around on various planets, but you discovered that there was a way to escape being bound to \cVone{} as a ghoul, yet retain your long lifespan. In fact, it was possible to take on the nature of the Ver and become their equal. Yes, you would have their need for blood, but it would not have to be blood of the Ver. You would be accepted as an equal among those who had held you captive all these years.

And wouldn't if be the perfect irony if you could have \cVone{}'s job! The Ver, like any civilized society, respected the law of the duel. If you were to manage to take on a Veran nature and challenge \cVone{\them} to a duel and win, you would have \cVone{\their} position! The TIS Chivalry would be yours to command and the other pompous asses who have looked down on you over all these years would be subordinate to you! Of course, even if you couldn't get \cVone{}'s position, you would settle for winning one of the other Ver officers' positions. In order to do this, you will have to acquire a weapon somehow. One downside of being a slave is that you are generally not allowed to have access to weapons. And even if you can't manage to get an officer to agree to a duel, you find yourself still itching for some good combat. Perhaps you could find someone else to agree to duel you. And if duels fail to get you a job, there is another position currently open, given that the ship's Intelligence Officer was taken by humans during the last raid on Earth.

But you mustn't get ahead of yourself. There is still much to do before you can win your rightful place aboard the ship. Using your feminine wiles over the course of decades, you have gradually convinced \cVtwo{}, the ship's Engineering Officer, that you are in love with \cVtwo{\them}, and that the only way you can truly be together is for \cVtwo{} to turn you, giving you the Veran nature. The process is obscure and complex, so it took \cVtwo{} quite a while to learn how it was done. But \cVtwo{} has finally agreed to do it, and has begun the four day process. Today is the final day of the transformation. You do not have the nature of the Ver yet, so you must do all you can to ensure that the final day goes smoothly. Unfortunately, there is confusion aboard the ship that could interfere with the delicate and dangerous process. The TIS Chivalry is passing through Frith space, which is controlled by a sort of alien police force, intent on discovering your distinctly illegal cargo of humans. Usually there is no trouble from them, but there are whispers of problems, and today there is a new potential ghoul aboard the ship, one who is not cooperating. There is also a human who \cVthree{}, the Medical Officer aboard the ship, cannot put to sleep with the others. This could cause trouble, and trouble could interfere with your turning, which is quite time sensitive. Therefore, you should do what you can to ensure that everything goes smoothly as you pass into Ver space, ensuring that the proper actions are taken at the proper time.

Unfortunately, these moderate inconveniences are not the only things that could go wrong. There's also the not-so-tiny matter of how you convinced \cVtwo{} to turn you... See, \cVtwo{} is in love with you, which you have used to your advantage. There is a strong taboo against mixed Ver/human relationships, which are viewed as something akin to bestiality in Ver society. So you have convinced \cVtwo{\them} that the only way you can be together is if \cVtwo{\they} turns you, so you can be considered equals in the eyes of the Ver. There are multiple problems with this. The first of which is the fact that \cVone{}, your "owner," knows nothing of this arrangement, and presumably wouldn't be very happy to lose one of \cVone{\their} slaves. But perhaps the most pressing problem is that you are not really in love with \cVtwo{}, and have no intention of staying with \cVtwo{\them} after the turning process is complete. \cVtwo{} is a loathsome control freak, always desiring to be the dominant partner in the relationship, which infuriates you to no end. You have always preferred to be the dominant partner, or at least be on an equal playing field. You simply won't submit to trading one form of enslavement for another. But how will \cVtwo{} react when \cVtwo{\they} realizes that you played \cVtwo{\them} like a fiddle, or \cVone{} when \cVone{\they} realizes that you are no longer \cVone{\their} slave? You're going to have to think on your feet. Perhaps the confusion of the day can be used to your advantage...

Another bit of information that you may find useful is that \cVone{} has a special ring that allows for control of the TIS Chivalry, enabling one to bypass the blood-based controls that can determine the identity of the user. You know \cVone{} never takes it off, but if you were to somehow get ahold of it... perhaps you could come up with something.

But first things first: In order to ensure that your turning is completed, you are going to have to continue with the ruse that you are in love with \cVtwo{\them}. It is unlikely \cVtwo{\they} will agree to continue the procedure if \cVtwo{\they} discover that you are not actually in love with \cVtwo{\them}. In fact, you are actually in love with \cJoan{}, another ghoul aboard the ship. She's been aboard longer than any of you, and was one of the first people you saw after being brought aboard. She was always quiet and obedient, but there was still a sort of spark behind her eyes that drew you in. There was also the fact of her beauty, which she didn't seem to notice. And when you found out who she really was, the heroic, determined Joan of Arc you had heard stories of as a young girl, that was all it took. You fell in love with her, but have kept your feelings hidden as long as you have had to keep up your "relationship" with \cVtwo{}. You have finally written a love letter to her, and hope to finally be able to confess your love to her. Upon your freedom... or before things go to hell, you want to deliver the letter to her. You will never forgive yourself if you don't find out whether she returns your affections.

But before you do anything, you must do the next step towards your turning. \cVtwo{} has told you that you need to have your blood tested by \cVthree{} and bring the results back to \cVtwo{\them}, without letting on what you're doing. This shouldn't be difficult, as \cVthree{} is obsessed with blood and is collecting blood samples anyway. It shouldn't be too hard to hang around \cVthree{\them} until \cVthree{\they} ask you to provide a sample.

After that, there should only be a few more steps before you have the Veran nature and can decide your fate. By the time this night is over, your life will have changed irrevocably, for the better or for the worse, depending on your actions. You feel more excited than you have been in decades.

\begin{itemz}[Goals]
	\item Get your blood tested by \cVthree{} and bring the results to \cVtwo{}.
	\item Follow the next steps of the turning process and keep other situations from interfering with it.
	\item Try to assist in containing the non-sleeping human and the new ghoul so the inspection goes smoothly.
	\item Until you have the Ver nature, convince \cVtwo{} that you are still in love with \cVtwo{\them}.
	\item When you are Ver, find a weapon and arrange a duel for \cVone{} or one of the other officers' positions. If this doesn't work out, arrange a duel with someone else.
	\item If a duel for a position doesn't work for you, try to convince \cVone{} to give you the Intelligence Officer position that recently opened up aboard the TIS Chivalry.
	\item Deliver your love letter to Joan, preferably after you've been turned so \cVtwo{} can't find out and stop turning you.
	\item Avoid retribution from \cVone{} and \cVtwo{} for your actions. This may get bloody.
\end{itemz} 

\begin{itemz}[Notes]
	\item 
\end{itemz}

\begin{contacts}
	\contact{\cVone{}} - The Ver who owns and commands you. \cVone{\they} considers you a pampered pet. You want \cVone{\their} position.
	\contact{\cVtwo{}} - An officer of mechanical science aboard the TIS Chivalry, who is convinced that you are in love with \cVtwo{\them}, though you are not. \cVtwo{} is currently going through the process of turning you, contingent on your love for \cVtwo{\them}.
	\contact{\cVthree{}} - The medical officer aboard the TIS Chivalry. \cVthree{\They} is interested in collecting blood for scientific reasons. You need to get your blood tested by \cVthree{\them} and get the results to \cVtwo{}.
	\contact{\cJames{}} - A ghoul aboard the ship who "arrived" a few hundred years after you. He is much younger than you, but looks like and old man. He is also interested in the science of blood. Perhaps you could use him as a back-up if you can't get your blood tested by \cVthree{}.
	\contact{\cRasputin{}} - A ghoul aboard the ship who arrived hundreds of years after you. A strange fellow whose interests diverge rather dramatically from yours. He loves spending time with dusty old books as opposed to people.
	\contact{\cJoan{}} - The ghoul you have fallen in love with. You want to confess your love to her. 
\end{contacts}

\end{document}

