\documentclass[char]{guildcamp4}
\begin{document}
\name{\cPilot{}}

Born into a long line of pilots, deep space pilots. 

More is of course needed to explain why this is such a great and terrifying thing.
Those who navigate the courses in the emptiness of space have long and discretely payed homage to Lurker at the Threshold. It is a being older than time that is beyond the threshold of your reality, looking in, watching and knowing all. Thus you and your family have for generations been members of the cult of Yug Sothoth. However, years ago the powers in your government found relics of past worshipers, from before even the Frith. Those who attempted to study these artifacts found their minds swiftly stripped bare, or inundated into oblivion, or other even less pleasant ends. This lead to the artifacts, and even the worship of anything similar something to be quietly hushed up and locked away. 

Those of your kind were thankfully warned ahead by the Opener of the Way to keep the worship secret, discreet, hidden from prying eyes and ears. 
In fact, it is the rather hilarious secret that every successful Frith Deep Space pilot is a worshiper, for the rewards given help keep the mind clear and sane when dealing with the terrible void between stars. You were one of the best of this set, able to almost feel the patterns of gravity to skim along where others would need to fight the void. Your travels led to you meeting a human who was also a fellow worshiper of Yug Sothoth.  Love bloomed between you and \cAlice{}, a love that spread to the children you both adopted. 

However, you made a mistake in your personal curiosity; you looked into a facility where some of those artifacts of your worship are stored. Caught in the midst of snooping into the building, you were sentenced to 5 years of corrective action. Since then you have had your piloting skills used by the customs officials of the Frith, as well as your ability to intercept ships and dock smoothly regardless of the willingness of the other party. 
You have this one last run and then you will be free, free to be with your family, free to fly where you wish in the welcoming void. FREE. 

\begin{comment}
\begin{itemz}[Backstory]
    \item A pilot who committed a crime, and is now on probation.
    \item Helping law enforcement as community service / rehabilitation / reintegration.
    \item Has human spouse, sympathetic to humans. Could lose kids if violates parole.
    \item Shares cult religion with Rasputin. Wants to further cult's goals.
    \item Religion's goal is to know everything. Got caught snooping where he/she shouldn't have been. Sent to prison for indeterminate amt of time.
    \item All Yog'Sothoth-related activity is illegal in Frith space.
\end{itemz}
\end{comment}

\begin{itemz}[Goals]
	\item Prove yourself as an upstanding, law-abiding citizen to \cCbad{} and \cCgood{}.
	\item Help any humans you might encounter.
	\item Further the goals of your cult.
	\item Avoid picking up a gun as that would lead to your release being revoked.
\end{itemz}

\begin{contacts}
	\contact{\cCbad{}} The senior officer whose ship you are flying. Somewhat jaded.
	\contact{\cCgood{}} \cCbad{}'s subordinate. Very eager.
\end{contacts}

\end{document}
