\documentclass[char]{guildcamp4}
\begin{document}
\name{\cPlead{}}

\begin{center}{\bf Test Subject to Food to Servant}\end{center}

Born to a simple family of farmers on Earth, you took part in a survey about where they took some of your blood. Next thing you know your parents are being offered a "generous payment" for the right to make you a "ward of the state" in the name of the greater good. You are being sent to a place with white walls and many needles. You meet \cSpite{}  here, as one of the many white-clad figures with needles that are constantly taking from you bit by bit, instant by instant, drop by drop. 

Well... simple family of farmers is rather misleading. Your family have long through the generations been worshipers of the Lurker Beyond the Threshold, Yog Sothoth, a being of great knowledge who rewards those who show it both respect and a drive for learning. In fact, the reason for your family giving you so easily was to give you a chance at finding where those men in suits would lead. Yog Sothoth had shared with your elders that you would not end your time in the hands of these men in suits. This was a chance at learning secrets that no true follower of The Opener of The Way could refuse. 

While you did not expect to be treat like royalty, torture is the only word that can describe what you have gone through. Needles, so many needles. Still you stayed, needing to learn the secrets of the agency, why they decided that the torture of fellow humans is neccessary, what are they trying to find. There is whispers of the word Ver, something about infiltration.

There is a crashing, and the next thing you know you are being taken somewhere alongside \cSpite{}. You come to locked up in a room with \cSpite{} locked across from you. You overhear one of your captors saying that you are not worth being made a ghoul, a member of the crew from what you can tell.

\begin{itemz}[Goals]
	\item Avoid being put into stasis
	\item Become a ghoul, or even a Ver, on the ship
	\item Perform a prayer to Yog Sothoth
	\item Follow the tenets of Yog Sothoth
\end{itemz}

\begin{itemz}[Notes]
	\item 
\end{itemz}

%\begin{contacts}
	%\contact{\cTest{}} <- This is the format for contacts 
%\end{contacts}

\end{document}
