\documentclass[char]{guildcamp4}
\begin{document}
\name{\cRasputin{}}

\bigquote{``Ignorance is the curse of God; knowledge is the wing wherewith we fly to heaven.''}{- William Shakespeare}

Knowledge is power, or so they say. It is too bad that knowledge is not freedom, or perhaps you would not be a slave cursed to serve for eternity. Perhaps it could become freedom for you, if you are to use it carefully... for blood begets knowledge, knowledge begets power, and power begets freedom. And blood... blood courses through your body and your life, the blood of two worlds, blood of knowledge and blood of power. You must seize it and make sacrifice, and then, only then, will you find your true place in life.

You were born in 1869 on the vast plains of Western Siberia to a well-to-do peasant family. You were the fifth of nine children, all of whom died but you and your sister Feodosiya. The townspeople never accepted you. In fact, they instinctively feared you and your unusual gifts. You've always been abnormally strong and healthy, healing much more quickly than an ordinary person, and you've always had a taste for red meat, the bloodier the better. When you were 18 years old you married and had three children, but the married life never suited you. You wanted something more. In 1892 you left your family to spend time in a monastery, where you became a fervent believer in Russian Orthodoxy. You became convinced that you must give up consuming meat and alcohol, which weakened you, but your religious fervor covered this up. Eventually you became a wandering religious mystic. Hundreds came from all around to hear your interpretations of the scriptures. Always you sought knowledge, and eventually you sought it beyond the walls of Orthodoxy. In your travels you discovered the cult of Yug-Sothoth.

At first you were hesitant to worship a deity other than the Christian God, but when you petitioned Yug-Sothoth for knowledge with a gift of blood, you received the answers that you had always been looking for. You heard a voice telling you the secret of your powers. The one you called father was not your true father, but in fact your father was a member of a vampiric race from a distant star known as the Ver. You learned that you would be strengthened again if you were to consume red meat and blood, and you began doing this again in secret and regained the strength of your youth. 

Around this time you were able to use your charm and influence to gain audience before the House of Romanov. The Romanovs were embroiled in dealing with the revolution, and the apparent weakness of the Tsaesarevich Alexei, the Tsar's son, only contributed to their problems. So you were taken on as healer to Alexei, who had hemophilia, a disorder of the blood that made him bleed profusely if injured. You gave sacrifice to Yug-Sothoth to gain healing knowledge to ease Alexei's suffering, which sealed your bond with the Tsarina, despite the hatred directed towards you from outside the palace after an initial fascination with your powers. The people were just like the ignorant peasants in your hometown, fearing what they did not understand. Ignorance makes animals of men, and you want to avoid ignorance at all costs. They tried to kill you more than once, and the last time they nearly managed it.

In 1916, the nobleman Felix Yusupov invited you to his palace, where he tried to poison you. He got you drunk and shot you multiple times. Strengthened by the red meat you ate in secret, this did not kill you. You made your way outside, only for one of Yusupov's conspirators to shoot you even more. Still you lived. Thinking you dead, the men wrapped your body in a cloth and dumped it into a hole in the ice above a nearby river. You have few memories of this time, during which you were scooped from the water and revived by the Ver, who left behind a copy of your form to convince those who sought to kill you of your death.

You woke up aboard TIS Chivalry, a Veran merchant vessel, where \cVone{} fed you a glass of \cVone{\their} blood. \cVone{\They} held your jaw in an inhumanly strong grip, tipping the glass so the blood fell down your throat in a stream. You gagged and choked at first out of shock, but then realized that it was quite pleasant on the tongue, and without thinking you simply drank the rest. Unbeknownst to you at the time, this bound you to be \cVone{\their} slave, a ghoul dependent on \cVone{\their} blood for your continued survival. Charged to serve as a crew member on TIS Chivalry and provide the Ver with a source of blood, you have spent the last hundreds of years in \cVone{}'s service. Yes, there is a great advantage to being a ghoul. Your lifespan is greatly extended by drinking Veran blood. You find yourself somewhat torn by your mixed nature though, unsure whether you should remain loyal to humanity or your Ver side. You find yourself unsure where you lie, as the Ver think of you as an inferior, and the humans met you with fear and revulsion.

Your tasks aboard TIS Chivalry were generally dull in between raids on Earth, mostly involving routine ship maintenance. But during the raids you would assist in subduing and transporting humans between Earth and the Veran homeworld. You found this distasteful, but having felt the strength in \cVone{}'s arm, you always followed orders. \cVone{} was never violent toward you, treating you more as a pet than anything else, but you weren't going to take your chances, even with your strength. In the years after you would come to be glad that you didn't try anything risky, as you eventually discovered just how powerful pureblood Ver really are.

In your early years aboard TIS Chivalry, you were able to discover that your father had once been a crew member of the ship, but that he had since moved on to other things on the Ver planet. You have no particular interest in meeting him, though you are interested in learning more about what your hybrid nature entails. You learned quickly that there is a stigma against hybrids of human and Veran descent, and that \cVthree{} harbors a great hatred towards hybrids, wishing them dead. You fear to think what would happen if he were to learn of your parentage. So you have done everything you can to hide this fact. Ideally, you would wish to live openly among the Ver of TIS Chivalry. Perhaps you could convince \cVone{} to order the acceptance of hybrids aboard the ship. This seems unlikely to convince \cVthree{} though, so perhaps you could orchestrate some means of getting his title and authority revoked, so he would be transferred off the ship at next docking with the Ver planet. You know that \cVone{} and \cVtwo{} hold no particular enmity towards beings like yourself, and while they may not completely respect you, they certainly would not kill you for being what you are. In the meantime, you must continue avoiding \cVthree{}'s incessant attempts at collecting and testing your blood. If your blood is sampled by a Ver, your parentage would be revealed, putting you in mortal danger.

In order to hide your parentage, you have developed a working relationship with \cJames{}, one of the other ghouls aboard the ship, to produce a serum that hides your nature from Veran notice if they were to think to examine your blood. You have not had your treatment for nearly a week, and it is beginning to wear off, so you need to acquire and take it within the next four hours, or else risk exposure to \cVthree{}.

While \cVone{} finds you an amusing servant and companion, \cVone{\they} do not see you as anything close to an equal. Ideally, you wish to have a role at his side as a trusted officer. \cVone{} recently lost an Intelligence Officer to a mob of humans on Earth, so this position seems ideal. You have never heard of a hybrid attaining such a role, but perhaps you can use knowledge attained from Yug-Sothoth to convince \cVone{} of your utility. This would require a greater working, which would mean you would have to work with another of the Cult of Yug-Sothoth to complete the ritual. You know of no other members of the Family aboard TIS Chivalry, but there is always the chance that you will encounter other members if the ship docks with another. Keep your eyes open. You will likely want to inquire with \cVone{} of what kind of action or information would convince him to make you an officer. If you manage to become an officer, that would certainly give you a measure of protection against \cVthree{}, though ideally you would like \cVthree{\them} deposed from \cVthree{\their} position.

Even if you don't manage to acquire an officer position, you still wish to perform a great working with another of the Cult. At the very least you will gain knowledge, which you crave. At most, aside from gaining the Intelligence Officer role, you could gain knowledge that could persuade \cVone{} to remove \cVthree{}'s title and power, or convince others to protect you if you were to live openly as a hybrid, whether by providing information they want or through blackmail. You also know that \cVone{} has a ring that allows anyone wearing it to command the ship. This knowledge may be useful in your quest.

Right now TIS Chivalry is passing through Frith space, ruled by an insectoid race who intends to inspect the ship before you pass over into Veran space. You know that there is some trouble going on in restraining all of the humans that are to go up for sale on Ver, and that there is a new recruit to be made one of \cVone{}'s pets. Perhaps among this influx of others you could find another Cultist. It also provides an opportunity to prove your utility to \cVone{} if you can help the inspection go smoothly and convince the new potential ghoul to cooperate. 

You feel no loyalty towards the majority of humans captured by the Ver, but would find kinship in another of the Cult. Though he is not a Cult member, you value \cJames{} for the serum he provides you and find his scientific pursuits honorable. He has kept your secret for you over the years, so he is the closest thing to a friend that you have aboard TIS Chivalry. You will want to remain in his favor to continue receiving his treatments. As for the female ghouls aboard the ship, you simply tolerate them. \cJoan{} has simply lost her mind, and is prone to lunatic ravings. You know she has visions, but you know many of them to be false, as they contradict the knowledge given to you by Yug-Sothoth. She is a gloomy, insufferable moralist and unpredictable in her emotions. You know that she would think poorly of your dealings with Yug-Sothoth, so you will do what you can to prevent her from learning of them, lest she do something unfortunate. As for \cJulie{}, she is nothing more than a violent degenerate, only interested in physical comforts, knowing little of the pursuits of knowledge. You have few dealings with her, and don't see her as much of a threat to your actions. You doubt she could comprehend them.

Overall, this voyage seems promising in helping you to attain your goals. Use your cleverness and knowledge to work towards them, using the unusual situation to your advantage.

\begin{itemz}[Goals]
	\item Convince \cVone{} to make you an officer aboard TIS Chivalry.
	\item Find members of the Cult of Yug-Sothoth with whom to perform a ritual to gain knowledge.
	\item Figure out a way to live openly as a hybrid aboard TIS Chivalry.
	\item Get \cVthree{} removed from \cVthree{\their} position so \cVthree{\they} will no longer pose a threat to you.
	\item Get this week's serum from \cJames{} and take it.
	\item Convince the new potential ghoul to cooperate with \cVone{}.
	\item Don't let any Ver take a blood sample from you unless you have taken the serum.
	\item Keep your dealings with Yug-Sothoth a secret from Joan.
\end{itemz}

\begin{itemz}[Notes]
	\item 
\end{itemz}

\begin{contacts}
	\contact{\cVone{}} - The Ver who owns and commands you. You require the blood of his kind to survive. You are on good terms, given these facts, though he does not see you as an equal. You hope to convince him to give you an officer role, raising your position in his eyes.
	\contact{\cVtwo{}} - The Engineering officer aboard TIS Chivalry, another Ver. You have no strong feelings about \cVtwo{\them}. \cVtwo{\their} rank is below \cVone{} and above \cVthree{}, which may be useful information.
	\contact{\cVthree{}} - The Medical officer aboard TIS Chivalry. \cVthree{\They} hate hybrids and wish to collect blood samples for scientific purposes, which could reveal your parentage and put you in danger. You want to avoid \cVthree{\them} and get \cVthree{\their} position revoked.
	\contact{\cJames{}} - Another ghoul and the closet thing you have to a friend. He provides you with the serum that hides your true nature from the Ver. 
	\contact{\cJoan{}} - A ghoul aboard the ship. A moralist lunatic. You wish to avoid letting her learn of your dealings with Yug-Sothoth.  
	\contact{\cJulie{}} - A ghoul aboard the ship. A loathsome degenerate. 
\end{contacts}

%wants to help descendent - mem packet
% mem packet - you don't

\end{document}

