\documentclass[char]{guildcamp4}
\begin{document}
\name{\cSpite{}}

You grew up surrounded by books. Your parents were successful agricultural biology researchers, and the walls of your home were always lined with dusty shelves and filing cabinets. Every few years, your family would pick up and move to yet another rural college town in the middle of nowhere. You hated it every time. You didn't care if {\bf this} new town was home to a prestigious agricultural research institute; all you knew was that you were going to be the new kid in school, yet again. Moving always meant starting over with no friends, and gradually losing touch with the few friends you had just barely made. Other than your parents, whom you grew very close to, the only constant in your repeatedly-uprooted childhood was the growing library of books that they could never bear to get rid of. So, you immersed yourself in reading them. You had no choice; there was nothing else to do.

You don't know whether it was because you started reading plant microbiology textbooks when you were so young, or whether you always had it in you, but it turns out that you really had a knack for the life sciences. If you couldn't find an answer to something that you were curious about, you designed and carried out your own experiments in your garage. You won national science fairs and scholarships to universities that you had never even heard of. By the time you finished junior high, colleges were begging you to skip years of high school coursework to enroll early. 

Then, one day, your parents never came home. You remember it vividly -- you were 14, it was a Sunday, and you were packing for college. They had gone to church, which was something that they thankfully spared you from, and night fell without a word from them. Calls went unanswered. The police were unhelpful. It was only 72 hours later that the missing persons investigation could begin in earnest. The search was called off a month later. The church that your parents had told you about (but never taken you to) didn't exist. Their case was never solved.

You were never one to take ``I don't know" for an answer. You leveraged your considerable intellect, public sympathy, and family friends. You wouldn't give up. {\bf Someone} had to know {\bf something}. Eventually, one of your parents' colleagues cracked, perhaps taking pity on you, or perhaps feeling that you deserved to know. They explained that your parents had been involved with a cult of Ver-worshippers called the Blood Pact. On that fateful Sunday, every last member of the Blood Pact had disappeared. Investigators uncovered encrypted communications between the Blood Pact and the Ver, showing that the Ver had promised their human followers eternal life if they would board one of their ships and pledge their service to them. 

Somehow, you moved on. You grew to hate your parents -- for never telling you the truth, for not even saying goodbye. And by extension, you also hated the Ver, for taking them away from you. Immersing yourself in your studies, you became a successful biomedical researcher in your own right. You cured leukemia and became a tenured professor by 25. But despite your successes, you were never happy. Everything had changed that day, and nothing could ever make it right.

One day, you received a message from an unidentified sender. All it said was ``Talk to us if you want to do something about the Ver." Of course, you responded. It turns out that you weren't the only one who hated the Ver. There was a shadow organization, as well-funded as they were cryptic, who saw the Ver as an existential threat to all of humanity, and were looking for ways to prepare for inevitable all-out war against them. Their mission was to counteract the Ver threat by any means necessary. ``By any means necessary." The words seemed to burn on your display, like fire. And the kicker -- they wanted you to work for them.

You continued your hematological research, this time with the considerable resources of the shadowy anti-Ver organization at your disposal. While reviewing the results of a massive blood collection effort, you discovered that one subject's blood exhibited remarkable properties. You were able to convey the importance of this particular person,\cPlead{\MYname}, to your patrons, and they agreed to ``procure" \cPlead{him} for your studies. 

But then it all went wrong. The Ver found out about the opposition group, and launched a surprise raid against your hidden base. They captured you and your research subject, and now you're both locked aboard a Ver ship bound for Ver space. You can't even begin to imagine what unspeakable horrors await you, but the crew seems to be distracted by a Frith ship hailing them. Now's your chance to try to get free. If you can manage that, maybe you can do something about your situation...and maybe even try to make things right.

\begin{comment}
Grew up sheltered. Family of academics. Surrounded by books, leading researchers, and rich sources of information. Childhood prodigy. 
Parents were researchers who never quite let on what they were studying. You know it had something to do with blood. Became fascinated with the Ver. Made contacts with them. 
When you were 14, parents disappeared. Everyone tried to keep you from finding out the circumstances, but you would not be dissuaded. Using resources, you found out that they were part of a Ver-worshipping cult. Made deals to be turned into ghouls and be granted extended lifespans. Longer life = more opportunities for research.

Moved on. Hated parents because they didn't even say goodbye. Became successful researcher in own right. University professor. Recruited by covert anti-Ver branch of government to conduct research. Found something weird with \cPlead{}'s blood while doing a routine study. Got XCOM to abduct him for further study.
One day, discovered confidential files detailing the fate of the Blood Pact (Ver-worshipping cult). Turns out the Ver tricked them. Assured parents that you would be ghouled as well, but once they were aboard, shoved into stasis pods and turned into brain-dead blood puppets. Left without you ever being alerted.
Now you hate all Ver with a passion. One day, abducted by \cVone{}, along with research subject \cPlead{}. Now, you have a chance to find out more. And maybe even make things right.

\begin{itemz}[Backstory]
\item A renowned modern human biomedical researcher. Cured leukemia. Ostensibly an academic researcher, but also part of a covert government anti-Ver organization.
\item While conducting a study analyzing routine blood samples, discovered extraordinary properties in \cPlead{}'s blood. Managed to get \cPlead{} abducted for further study.
\item When little, parents were lured by the promise of extended lifespan. Volunteered to join the Ver as ghouls, abandoning \cSpite{} as well as their lives on Earth. However, as soon as they left human space, they were turned into blood puppets: brain-dead sources of human blood, a delicacy for the Ver.
\item Vowed to do everything he/she could to bring down the Ver. Became an eminent biomedical researcher. Recruited to join a covert anti-Ver government organization.
\item Hates Ver with a passion and would rather kill everyone on board, including him/herself, rather than be turned.
\end{itemz}

\end{comment}

\begin{itemz}[Goals]
	\item Destroy Ver, even if it requires collateral damage and personal sacrifice.
	\item Survive and escape.
	\item Sabotage the ship's engines.
	\item Find out more about the Blood Pact. Who are the Ver involved, and who tricked your parents?
	\item Hold off \cVone{} from turning you into a ghoul. You have multiple options:
    	\begin {itemz}
    	\item Present research to \cVone{}. You don't want to give away real secrets, so make stuff up.
    	\item Create a disorienting drug using equipment in the bio lab to confuse \cVone{\them}.
    	\end {itemz}
	\item Discover what is strange about \cPlead{}'s blood.
	\item Investigate Ver cloaking technology.
	\item Investigate Frith secret technology.
\end{itemz}

\begin{contacts}
	%\contact{\cTest{}} <- This is the format for contacts 
	\contact{\cPlead{}} a human research subject that you were experimenting on. 
\end{contacts}

\end{document}
