\documentclass[char]{guildcamp4}
\begin{document}
\name{\cVone{}}


\textit{Come here my pretty little pets.}

You are one of the Ver, a race that has been traveling the stars for many thousands of years. You were born into a very wealthy family, taught from a young age how to conduct business, negotiate deals, and generally slide smoothly through the worlds. Your family has long conducted trade under Imperial Charter, which gives them the privilege of traveling freely through Ver space, as well as the right to leave Ver space at will. As a part of this privilege, you are required to share a larger part of your profits with the Imperial Throne than other merchants. This inconvenience is offset by the fact that you are a sanctioned Imperial Ship, which has saved your ship on more than one occasion; any illegal search and seizure would summon the might of the Imperium to investigate. You were gifted your current ship, The Imperial Ship Chivalry, upon signing a life-long contract to supply the Empress's court with fresh supplies of the delicacy that is Kine blood. You discovered the Kine homeworld when the Kine were naught but crude hunter-gatherers, and were given a monopoly over the supply of Kine blood. No other Ver may intrude upon the supply of Kine so long as you continue to deliver, which is a duty that you have been faithfully fulfilling for the last several thousand years. You watched as the Kine developed from primitive tool-users to beings that may actually be worth recognition. 

The Kine even managed to create a rather quaint recreation of the Empress's court during what they refer to as the Victorian age. It bore such a striking resemblance that you decided it would be entertaining to rename your ship officers' titles to mirror their so-called nobility. Your officers have gone with this, perhaps thinking you are eccentric, but no more than they themselves are. In fact, you have found it a rewarding course to enlist officers who are competent, but rejected by others for having quirks. You have built a reputation for being accepting of those whom others curse for being weird, and in exchange have found a loyal cadre of officers. \cVtwo{} is an excellent engineer, but not very good at denying sudden urges, and also has an odd fascination with pain. They graduated from the Naval School, but would have barely survived the indebted years of service to the Navy. However, you do need to keep an eye on them as far as your pets are concerned, for \cVtwo{} is not good at holding back with punishments. \cVthree{} is an outstanding medical officer, with one of their quirks being a fascination with the study of blood. You tolerate their studies, since those studies may in fact lead to a profit at some point, and even if not, their study is not an especially costly diversion for an officer to have. You used to have a skilled intelligence officer, who was unfortunately lost in the last raid due to a misunderstanding, and now you need a new one: someone whom you can trust to ferret out secrets and help keep the ship running. Certainly not a simple ghoul; you doubt the officers would stand for going that far.

As far as your crew, you found a way to turn your own fascination with the Kine into a way to keep your ship running smoothly. Every so often, you find a member of the Kine that amuses you especially: something they accomplish that raises them above their kin. Take \cJoan{} for instance: such a lovely little flower of zealotry, thinking that this is \cJoan{\their} personal Hell that \cJoan{\they} must suffer and serve through. Considering the whole attempted burning-at-the-stake business, you can understand the misunderstanding. These special Kine deserve to be preserved as your pets, kept both alive and loyal with offers of your blood, without which they would soon age and die. That you do give them a minor wage in credits serves more to keep the books clean for the Frith.

Now the Kine have expanded into an interstellar power, brokering treaties with the Frith. Even worse, your enemies in the court back home managed to convince the Empress to sign a treaty forcing the observance of each race's laws while in their space. Some of the Ver wish to both destroy the power of your family and create a war with the Kine that would lead to their complete subjugation and taming as a source of blood for all. Those Ver are fools. You have studied the Kine long enough to know that such a war would simply lead to the extinction of the Kine; the Kine barely tolerate being ruled by each other. They would commit suicide as a race before being brought to heel. However, owing to the treaties, you are still able to trade Kine blood legally in the form of blood packs. Blood that, even when stale, is more delicious than any other found so far--some would even say addicting. 

Thankfully, you have been able to find Kine over the years who would sell their Kine for money, power, or even promises of life eternal, which your blood can give. Some very few have allowed your ship to sneak onto Earth itself and procure several hundred Kine to take back to the Empress. This provides a convenient pretext for the Kine in power to tighten their control and institute martial law over their fellows, with you as the big bad threat and being paid a healthy commission. You even managed to get ahold of \cSpite{}, someone who managed to cure cancer of the blood (how lovely!), though \cSpite{\they} seem to be very resistant to the deal that the rest of the crew enjoys. No matter; you have time.

Wait--what? You have reports of a Frith customs ship hailing. They were supposed to catch us after we managed to drop off the cargo. \cCbad{} must be getting greedy, or just impatient. Well, \cVtwo{} knows to give \cCbad{\them} the money agreed upon.


 

\begin{itemz}[Goals]
	\item Keep your pets--the crew--alive.
	\item Smooth your way through customs; KEEP \cCbad{} alive.
	\item Win over \cSpite{} as a faithful ghoul.
	\item \cPlead{} interests you due to them not being able to stasis. Keep them alive. 
	\item Figure out who could serve as the Chief Intelligence Officer.
	\item Make sure that all of your pets have money on hand to prove they have wages just in case the officers do in fact check.

\end{itemz}

\begin{contacts}
	\contact{\cVtwo{}} The Chief Engineer of the Chivalry. Their given title is \cVtwo{\Marq}.
	\contact{\cVthree{}} The Chief Medical Officer of the Chivalry. Their given title is \cVtwo{\Baron}.
	\contact{\cJoan{}} One of your pets on board the Chivalry. One with much religious fervor.
	\contact{\cJulie{}} One of your pets on board the Chivalry. \cJulie{\they} constantly seem to want to fight or party, or both.
	\contact{\cJames{}} One of your pets on board the Chivalry. A fascinating example of the scientists from \cJames{\their} era.
	\contact{\cRasputin{}} One of your pets on board the Chivalry. The rumors surrounding \cRasputin{\their} work healing a royal family, and the attempt to kill \cRasputin{\them} is quite curious.
	\contact{\cSpite{}} A Recent capture, one you want to make a ghoul for \cSpite{\their} curing of blood based cancer.
	\contact{\cPlead{}} A recent capture, \cPlead{their} incompatibility with the stasis pods is interesting, but not enough to hold your interest. You don't consider them worthy of being a ghoul.
	\contact{\cIntel{}} The Former Chief Intelligence Officer of the Chivalry, their given title was \cIntel{\Count}.
\end{contacts}

\end{document}
