\documentclass[char]{guildcamp4}
\begin{document}
\name{\cVthree{}}

\textit{Blood is life, life is blood.}

You have an in-born fascination with life, which is a bit eccentric even among your fellow Veran scientists. If only they could understand you! Oh well, as the medical officer aboard The Imperial Ship Chivalry, you are given enough leeway to indulge in your curiosity. Though you never really understood how Chief Medical Officer translates to \cVthree{\Baron}, you are certainly not one to render judgment for being odd.

Your family was never truly influential in the politics of the court, but it was certainly well-off. A family that had stood since the founding of the Empire, servants to the Empress from the beginning, never seeking glory, only quietly supporting the throne. All undone in one night of fire. The authorities never caught all of the perpetrators, but those who were apprehended painted quite the deadly picture. Hybrids--freaks of nature that the common folk are not even able to conceive of, do not even know are possible, unstable threats to greater society--murdered your family for the support of the throne. The hybrids claim that they only wish to gain rights for other races, for the food, but you know better first-hand. They are nothing more than terrorists, driven by the conflict in their own blood. Self-destruction is their only end. 

Thankfully, the Empress rewards those who are loyal, so she put your family's estate in trust, making you a ward of the best tutors in the Empire. Your fascination with life, with the blood that makes life, was given free reign. You have studied the art of life well enough to qualify as a Medical Officer in the Imperial Navy, though the Empress herself mentioned you to \cVone{} in recommendation. You have found the years of service afterward highly rewarding. \cVone{} is odd, this is true, but \cVone{\they} have loyally fulfilled their duty to the throne for many thousands of years, which is something for which you have profound respect. That \cVone{} has allowed you to conduct your side research into life has been a blessing atop a gift. 

On the last raid, the former Chief Intelligence Officer, now lost to the void, whispered to you that \cIntel{they} had hints that a hybrid had managed to come aboard the ship. You know not who, but obviously any hybrids are a threat to everyone on board. You must stop them one way or another.

As if that was not enough, one of the Kine food animals seems to be incompatible with the stasis pods. You will need to test their blood to find out how to modify one of the pods so that \cPlead{they} can be put into stasis. After all, any Kine that has not managed to spark the interest of the captain, and thus earn a spot on the crew, has only one fate: a delicious end. 

\begin{itemz}[Goals]
	\item Get a stasis pod modified to put \cPlead{} into stasis though the Captain ordered that \cPlead{} be left out of it for now.
	\item Get a sample of everyone's blood and analyze it
	\item Keep \cJames{} away from your delicate instruments
	\item Get rid of any hybrids on board
\end{itemz}

\begin{contacts}
	\contact{\cVone{}Captain of the Chivalry, though \cVone{\they} prefer the title \cVone{\Duke} }
	\contact{\cVtwo{} The Chief Engineer of the Chivalry, their given title is \cVtwo{\Marq}} 
	\contact{\cJoan{} One of the pets of the \cVone{\Duke} on board the Chivalry. One with a fiery temper a much religious fervor} 
	\contact{\cJulie{}One of the pets of the \cVone{\Duke} on board the Chivalry. \cJulie{\they} is the love of your existence.}
	\contact{\cJames{} One of the pets of the \cVone{\Duke} on board the Chivalry. A annoying example of the scientists from \cJames{\their} era}
	\contact{\cRasputin{}One of the pets of the \cVone{\Duke} on board the Chivalry. The rumors surrounding \cRasputin{\their} work healing a royal family, and the attempt to kill \cRasputin{\them} is quite curious}
	\contact{\cSpite{} A Recent capture, one \cVone{} wants to make a ghoul for \cSpite{\their} achievement, curing of blood based cancer}
	\contact{\cPlead{} A recent capture, \cPlead{their} incompatibility with the stasis pods is interesting}
	\contact{\cIntel{} The Former Chief Intelligence Officer of the Chivalry, their given title was \cIntel{\Count}}
\end{contacts}

\end{document}
