\documentclass[char]{guildcamp4}
\begin{document}
\name{\cVtwo{}}

\textit{Such a lovely tapestry of control!}

You came from a lower family on the Ver homeworld with the bare minimum of support or schooling. You managed to score high enough on the Imperial Entrance Exam to earn a spot in the Imperial Naval Engineering School under contract with the Navy. You worked hard, bringing home passing marks, though catching a few demerits for lack of impulse control. After graduating, you were facing several hundred years of worthless work in the Navy patrolling empty space, when you received the offer of a position on The Imperial Ship Chivalry, a trading vessel that operates under direct Imperial Charter. These vessels are fairly rare, requiring the patronage of one of the High Families--close friends of the Imperial Throne, and known for leaving Imperial space and bringing back valuable goods directly to the throne! A bit more importantly, the Chartered vessels do not run under standard Imperial regulations. Thus, you are the Chief Engineer of The Imperial Ship Chivalry. 

As you have gotten to know your captain, or rather \cVone{\Duke}, as \cVone{\they} prefer to be called, you have noticed that \cVone{\they} are far in excess of the normal eccentricities expected of a chartered trader, but that works out rather well for you. You can play as though you were a member of Her Imperial Majesty's court, though the crew being a bunch of ghouls is just downright weird. If you did not have the videos on your terminal showing that their first drink was forced you would think this was actually a loyal crew.

Recently, the ship lost its Chief Intelligence Officer, the one who--to put it bluntly--was in charge of the bribes. The captain was able to maintain their contacts, but has delegated the actual payments of the bribes to you. This is something you find quite agreeable, since it gives you a chance to line your pockets a bit more. A little skimming never hurts!

After years in \cVone{}'s service, you had given up on finding ways to exercise your desires, when one of your captain's pets caught your attention. Seeing \cJulie{} in action was simply marvelous! The ability to fight so well, the drive, the sheer vitality. You must have \cJulie{\them}! Even here, on a ship far from home, \cJulie{\they} is full of fire. You have attempted to court \cJulie{\them} secretly (the captain is very protective of \cVone{\their} pets), and at first \cJulie{\they} spurned you, but that only made you want \cJulie{\them} more. Now, though, you have made your serious intent clear: you are not seeing \cJulie{\them} as a toy, but as someone whom you wish to turn into a fellow Ver. Your (do you dare say it) love seems to be being returned. \cJulie{} only needs to be drained and given your blood once more in order to become a full Ver. Then \cJulie{\they} will be able to witness a truly new world of sensation that you want to gift to \cJulie{\them}.

What? There is a Frith ship! But... you spent some of the bribe money at your last port... Hmmmm, perhaps you can scrounge up some from the rest of the crew; the Captain pays them to keep the books clean...

\begin{itemz}[Goals]
	\item Keep the ship running smoothly.
	\item Gather enough money to match the bribe required, 2000 credits.
	\item Sneak a bit of Frith technology, finding out what on the Frith ship let them find you.
	\item Turn \cJulie{} into a full Ver.
	\item Make \cJulie{} into your own submissive.
	\item Don't let anyone know about your turning of \cJulie{} until it is too late for them to stop it.
	\item Obey your \cVone{\Duke}'s orders if you must. 
\end{itemz}

\begin{contacts}
	\contact{\cVone{}} Captain of the Chivalry, though \cVone{\they} prefer the title \cVone{\Duke}.
	\contact{\cVthree{}}The Chief Medical Officer of the Chivalry. Their given title is \cVtwo{\Baron}.
	\contact{\cJoan{}} One of the pets of the \cVone{\Duke} on board the Chivalry. One with much religious fervor.
	\contact{\cJulie{}} One of the pets of the \cVone{\Duke} on board the Chivalry. \cJulie{\they} constantly seem to want to fight or party, or both.
	\contact{\cJames{}} One of the pets of the \cVone{\Duke} on board the Chivalry. A fascinating example of the scientists from \cJames{\their} era.
	\contact{\cRasputin{}} One of the pets of the \cVone{\Duke} on board the Chivalry. The rumors surrounding \cRasputin{\their} work healing a royal family, and the attempt to kill \cRasputin{\them} is quite curious.
	\contact{\cSpite{}} A Recent capture, one \cVone{} wants to make a ghoul for \cSpite{\their} achievement, the curing of blood based cancer.
	\contact{\cPlead{}} A recent capture, \cPlead{\their} incompatibility with the stasis pods is interesting.
	\contact{\cIntel{}} The Former Chief Intelligence Officer of the Chivalry, their given title was \cIntel{\Count}.
\end{contacts}

\end{document}
