\documentclass[blue]{guildcamp4}
\begin{document}
\name{\bChivalry{}}

The Imperial Ship Chivalry has been in the control of the Manfred family for several thousand years. The majority of this time it has been dedicated to bringing Kine cargo to the Empress. During most of that time the Ver on board would raid the kine populace with virtual impunity.

Recently the military power of the Kine around Earth has rendered other methods much more profitable. Now a days the Captain and Intelligence officer have cultivated a series of contacts within the Kine populace and even government who are quite happy to even abduct and sell their fellow kine in exchange for simple credits. The Kine would then be transfered without even leaving stasis into the hidden compartments within the Chivalry. 

The last run that TIS Chivalry conducted was extremely anomalous. Members within the kine government paid, and opened the way through, for the Chivalry to conduct a terror raid on the kine populace, specifically targeting the facility of a rival agency and the nearby civilian targets. 

You are aware that now, the two humans aboard the ship are imprisoned in a room aboard the ship until they can be dealt with. You can enter this room freely. The two humans are a person who cannot currently be put into stasis and one who is a potential new ghoul belonging to \cVone{}.

The Chivalry is now en-route to Ver space, being approximately 4 hours away from the border and thus being home free.


\begin{members}
	\member{\cVone{}} The Captain of TIS Chivalry
	\member{\cVtwo{}} The Chief Engineer of TIS Chivalry
	\member{\cVthree{}} The Chief Medical Officer of TIS Chivalry
	
\end{members}

\end{document}
