\documentclass[blue]{guildcamp4}
\begin{document}
\name{\bEarth{}}

Within the last few hundreds of years the home planet of Humanity has seen a very rapid movement towards development. Humanity has discovered how to travel the stars, and from there expanded outwards with great speed. Colonists seeking to find a better life elsewhere, hoping for freedom from the currently highly policed state that is now the Earth Government. Rapid development of the Kuiper Belt led to the springboard into a large military space fleet as well as a large civilian fleet, which in turn led to the creation of several highly patrolled colonies that while able to govern themselves, are constantly under watch by the Earth Government.

The Earth Government maintains extensive control over media sources, holding the idea that the safety of the state is equal to the safety of Humanity. This means that while there is extensive trade with other races such as the Frith, the amount of information on these races is sparse at best.

Frith, neighbors of Humanity, they established a peace treaty that involves each race following the laws of the government whose space they are traveling through. Hard exoskeleton means close quarters combat would be a bad idea.

Ver, Whispers of monsters that come in the night and take bad people away. Normally invulnerable to wounds. Exposure to UV light makes it possible to wound them, but also enrages them (+2 CR). This effect lasts for 15 minutes.


\begin{members}
	\member{\cPlead{}} Farmer
	\member{\cSpite{}} Scientist

\end{members}

\end{document}
