\documentclass[blue]{guildcamp4}
\begin{document}
\name{\bFrith{}}

The Frith are a peaceful race of expansionist spacefarers. After a period of rapid colonization, they now occupy the space between the humans and the Ver, as well as a significant portion of the galaxy. They share borders with many other species, and having to deal with a wide variety of alien cultures and dispositions has helped them to become experienced negotiators. They take great care to maintain friendly relations on each of their numerous fronts, to avoid becoming embroiled in tactically disadvantageous conflicts. The Frith were primarily responsible for negotiation between the humans, the Ver, and themselves, establishing regulations about which laws apply in each of their sovereign territories. For the most part, the three species have agreed that the local laws of inhabited space must be observed, regardless of a vessel's nation of origin. This has resulted in several diplomatic near-disasters involving transiting ships, as the normal, everyday practices of one culture may be considered downright illegal by others. For example, the Frith have outlawed slavery, as well as blood collection from unwilling participants, but such practices are deeply ingrained in Veran culture.
	
The Frith look mostly humanoid at first glance. However, since they originated from a jungle planet dominated by predators with piercing horns and tusks, they evolved subcutaneous chitinous plating to protect vital organs and extremities. This gives them a bulky, angular appearance, similar to a human wearing kevlar plates underneath all of their clothing. Their hard, high cheekbones and prominent eyebrow ridges make them look sulky and brooding, but also provide greater protection for their eyes. Their blood is more like an insect's hemolymph than mammalian blood, and as such, tastes disgusting to the Ver.

Born into a rigid caste system and ruled by a hierarchy of matrons, the Frith strongly believe in order and the rule of law. In fact there are many bloodlines that have shown exemplary service in their specific tasks with scientists stating that this is living genetic proof to the belief that one's blood decides one's role in life. The Frith hatch in clutches--dozens of genetically identical beings--each with the same predetermined place in society, and the same purpose to serve. The bonds between clutchmates seem to be almost incomprehensible, creating a sense of unity in each clutch that even is considered nigh absolute. However, the Frith worlds are not completely devoid of crime, as not every Frith is content to keep to the path that has been laid out for them. Perhaps due to their intimate familiarity with the effects of environment and upbringing on otherwise identical beings, the Frith have a keen, intuitive understanding of the differences between nature and nurture. They attribute problematic attitudes to unfortunate circumstances and life events, as evidenced by identical clutchmates who have managed to become productive members of society. As such, when dealing with criminals, the Frith prefer rehabilitation and reintegration over incarceration, seeing aberrant behavior as a problem to be solved, rather than mercilessly punished. A major case of this is the usage of parole programs where criminals are given corrective action in the for of carefully monitored jobs and limited freedom. Such parolees are not allowed under an circumstances to handle or obtain a weapon. 

Recently, trouble has been brewing in Frith space. Unknown energy signatures have been detected in the Human-Ver region, spurring the Frith to covertly develop weapons designed to be used against those two species as precautionary measures. High-amplitude ultraviolet pulses make the Ver temporarily vulnerable to conventional weaponry; however, this also enrages them. Potent human-paralyzing nerve gases have also been developed, while having no effect on Frith biology. As a particular note about the Ver, in Frith space it is illegal for any Ver to forcibly render another being into the state known as being a ghoul. 

As they've expanded their borders, Frith colonists have unearthed disturbing relics of ancient, long-forgotten civilizations. Their findings hint at an apocryphal belief system obsessed with the pursuit of knowledge, to the exclusion of all else -- a proto-religion that the Frith have dubbed the Unknowing. Many archaeologists and historians studying these artifacts have gone insane, and the objects themselves tend to go missing. As such, the Frith have outlawed all possession of Unknowing objects and re-enactment of Unknowing rites for the time being, until they can figure out what to do about them.






\begin{itemz}[Game Play Notes]
	\item Specialized cases of evidence 6413 which the number for if a person has no proof of gainful employment (that is they do not have money on their person) on your recording write the character number and 6413 as the other number.

	
\end{itemz}
	
\end{document}
