\documentclass[blue]{guildcamp4}
\begin{document}
\name{\bGhouls{}}

If you have this sheet, you are a ghoul aboard TIS Chivalry. A ghoul is a human that has been bound to a Ver by drinking this Ver's blood. Ghouls have a greatly extended lifespan, though this does not prevent them from being killed. Being made a ghoul does not impart a youthful appearance, though it can counteract frailty and physical weakness to some degree. In order to avoid aging, a ghoul must regularly drink the blood of the Ver who made them. In your case, this is \cVone{}, your owner and commander. If you go without \cVone{\their} blood for more than a few days, you will strongly crave it, begin to age, and lose any extra strength you may have gained from becoming a ghoul, at least until you are able to drink \cVone{}'s blood again.

Ghouls aboard TIS Chivalry are ordered to work as crew members of the ship. Though you are not compelled by your nature to obey your Ver masters, disobeying their orders could provoke dire consequences, such as them denying you the blood you need. Over the centuries you have generally learned to follow orders, even when this means you are to aid in the capture, subjugation, and transport of human slaves to the Ver homeworld for sale. As a ghoul, you are also a source of blood for the Ver aboard the ship. You have become used to them feeding on you, and will readily allow them to do so if you are ordered to provide a meal.

As long as you obey, \cVone{} will generally treat you as a valued pet, and will sometimes even allow you certain perks. Either way, you are paid a small salary so that things look good on the books if the Frith authorities check into things. You have to pass through Frith space on your way back from raids on Earth. Though you are slaves, you are ordered to act as if you are legal, free employees in the event that outside authorities board the ship. However, you will only ever be considered Kine (humans) to the Ver, who consider humans inferior beings. 

As you have lived aboard TIS Chivalry for several centuries, there are several things that are common knowledge to you. You all know that \cVone{} is the captain of the ship, and prefers to be referred to as the \cVone{\Duke}. \cVone{} is quite eccentric and values \cVone{\their} pets. \cVone{} has a ring that allows the wearer to control the ship's systems, bypassing the blood identification systems that usually control who is able to command ship systems. \cVtwo{} is the ship's Engineering Officer, a rank below \cVone{}. \cVtwo{} is to be referred to as the \cVtwo{\Marq}, on \cVone{}'s orders. \cVtwo{} as a very controlling Ver who is sometimes prone to mood swings and harsh punishments. \cVthree{} is the ship's Medical Officer, a rank below \cVtwo{}. \cVthree{} is to be referred to as the \cVthree{\Baron}, on \cVone{}'s orders. \cVthree{} is obsessed with blood and often likes to obtain samples for study from those aboard the ship. You also know that until recently there was a fourth officer aboard the ship, \cIntel{}, the Intelligence Officer, whose position has become vacant since \cIntel{\they} was taken by humans during the last raid on Earth. \cIntel{} was referred to as the \cIntel{\Count}, on \cVone{}'s orders. \cIntel{} was in charge of the bribes that allowed you to pass unscathed through Frith space.

The general procedure that allows you to pass through Frith space is as such: An arrangement was made with certain Frith that would allow TIS Chivalry to drop off their illegal human cargo before an inspection of the ship, which would reveal only a legal cargo of blood packs. After the sham inspection, the dirty Frith would receive a bribe. TIS Chivalry is equipped with unparalleled cloaking technology, which allows the ship to make the first drop of cargo without notice by Frith who are not in on the deal. As you have lived aboard TIS Chivalry for centuries, you are also aware of the fact that it contains two shuttles, Raid and Pillage, which are generally used for raids. They are generally locked down by blood identification technology when not in use for raids, though this tech can be overridden by \cVone{}'s ring. You have been ordered not to tamper with them unless ordered otherwise, such as for routine maintenance, during which a Ver officer will unlock the shuttles and allow you aboard.

At game start, it has just been discovered that there has been damage to the ship air supply. You must collaborate with your fellow ghouls to fix the air supply. If you do not manage to fix the supply within 15 minutes, your CR will be -1 for the rest of game, as the air will be thin.

\begin{itemz}[Goals]
	\item Fix the ship's air supply.
	\item Follow the orders of your Ver masters.
	\item If it has been a while since you have tasted Ver blood, acquire some from \cVone{} and drink it.
\end{itemz}

\begin{members}
	\member{\cJoan{}} 
	\member{\cJulie{}} 
	\member{\cJames{}} 
	\member{\cRasputin{}} 
\end{members}

\end{document}
