\documentclass[blue]{Pestilence}
\begin{document}
\name{\bKain{}}

If you have this sheet, you are a member of the Kain family, a distant cadet branch of the Startsev family. The Kain family is famous among the other spiritually powerful families due to their magical prodigy and innovativeness. However, their unorthodox research often garners suspicion, and few members of the Kain family have been elders. Rival families such as the Sidorovs have attempted to steal and replicate the Kains' magical research more than once. You are unsure what happened to the Sidorovs during the plague. They could be dead, or they could be alive and too proud to seek shelter at their enemy's home. Or they could have sent spies.

\cElder{\intro} jealously guards his research into binding earth spirits. No one outside the family knows the true source of \cElder{\their} powers, for the enslavement of an earth spirit would be considered dangerous and cruel by other families.

\cRebel{\intro} has also made forays into unorthodox magical research: \cRebel{\they} studies blood magic in hopes of finding a spirit-independent method of healing, and her research lead to the creation of a blood-generating device called the Crucible. The use of blood independent of the earth is normally considered taboo, so \cRebel{\they} has kept \cRebel{\their} research heavily guarded as well. Unfortunately, both the Crucible and \cRebel{}'s notes on blood magic haven't been seen since the shelter was established. Blood magic is highly dangerous and poisonous to the reputation of anyone who dabbles in it, so it is imperative that the notes do not remain in the wrong hands or worse, get published.

\cApprentice{\intro} has not conducted successful magical research as far as everyone is aware.

If you are loyal to your family, you will protect its interests and pursue these goals in addition to your own. 

\begin{itemz}[Goals]
	\item Find and retrieve the stolen notes on blood magic
 \item Find the Crucible
 \item Protect your family secrets
 \item Root out spies, enemies and traitors to your family
\end{itemz}


\end{document}
