\documentclass[blue]{guildcamp4}
\begin{document}
\name{\bVer{}}

The Veran Empire is one that has stood for many thousands of years. The direction of the Empress is held as absolute by all. As a hemophagic race they hold a poor view of any species that they feed upon, carrying an utter arrogance in their demeanor, with many animals that are held in their control only as sources of nourishment. The general policy is one of extreme isolation with the main contacts with foreign races being through Chartered Vessels. Ships that, while under the direct patronage of the Empress, are run by a very select number of families with imperial favor. The Imperial Ship Chivalry is one such ship that has been under the control of the Manfred family for thousands of years with the directive of supplying the Empress with the delicacy known as Kine blood. 

This delicacy was initially brought to the Empress by the Manfred family, who rewarded them with the sole contract for supply and rights to be the only supplier of this delicacy in Veran Space. Eventually the Kine developed sufficiently to create a treaty with the neighboring Frith, who have such distasteful blood. They were also sufficiently developed to be a hassle if provoked. Elements that sought to reduce Manfred influence convinced the Empress that the wisest choice for the Empire was to be included in the treaty that, among other issues, mandates that a those in Veran Space must follow Veran Law, those in Frith Space must follow Frith Law, and that those in Kine--or rather Human--space must follow Human Law. That slavery was outlawed by both species long ago was carefully not mentioned to the Empress until after the treaty was signed. This put the Manfred family in the poor situation of needing to provide the delicious Kine blood, without simply taking or buying slaves like they had done in the past. While the Manfred family has made do with buying blood packs from Kine in Kine space, their influence has taken a large hit.

The Ver are also notable for having the best stealth technology of any race, leading to further arrogance in what the Ver think they can get away with.

The Veran closely guard their weaknesses from other races. Veran are immortal so longs as they are not exposed to Ultra Violet Light, or more recently discovered, substances deemed "Holy Water" a chemical that seems identical to ordinary water, with no differences having been able to be detected beyond rendering the Veran victim able to be killed by normal trauma. 
Veran are unable to be wounded or knocked via combat mechanics with the following exception.

•	{\bf Exposure to UV or Holy Water.} Veran so exposed is now vulnerable to normal combat mechanics for the next 15 min, also the Veran's CR has a +2 modifier that also disappears after 15

Frith: Race of instectoid creatures with a hard exoskeleton, hard to penetrate in combat and with disgusting blood that provides no nutrients. They inhabit the space between Ver and Kine, and patrol it thoroughly.






\begin{members}
	\member{\cVone{}} The Captain of TIS Chivalry
	\member{\cVtwo{}} The Chief Engineer of TIS Chivalry
	\member{\cVthree{}} The Chief Medical Officer of TIS Chivalry

\end{members}

\end{document}
