\documentclass[blue]{guildcamp4}
\begin{document}
\name{\bYog{}}

\begin{center}{\bf Yug-Sothoth}\end{center}

{\bf Titles:} Lurker at the Threshold or Opener of the Way

The worshippers of the Lurker at the Threshold are quite varied, with many purposes and very few rules, carried with the previous tenet reigning over the later.

\begin{center}{\bf Laws}\end{center}

•	{\bf Tenet I.} Never dishonor the Opener of the Way. To do so is to invoke the Retribution of the Lurker at the Threshold   

•	{\bf Tenet II.} Never betray the Cult or its secrets. To do so is to invoke the Retribution of the Beyond-One. 

•	{\bf Tenet III.} Never kill a Dark Brother or Dark Sister. To do so is to invoke the Retribution of the Opener of the Way. 

The Cult recognizes no other laws divine or mortal. Though they have all learned the power of discretion and as such generally follow the laws of their locale in order to blend in amongst the unknowing. As Yug-Sothoth is the knower of all, their greatest drive is to know, whether that be by delving into arcane lore, creating an intelligence network to ferret out the secrets of a city, or as humble as working the local gossip mongers from behind the tavern bar. Knowledge for its own sake, or for power, Yug-Sothoth attracts many different kinds.

\begin{center}{\bf The Wrath of Yug-Sothoth}\end{center}

With a being that is far beyond mortal moral comprehension, one that in turn almost never turns its attention to any particular mortal, the Retribution of Yug-Sothoth is utterly unpredictable in its intensity or duration depending upon the judgment of Yug-Sothoth, though it is always swift in its implication and often involves the ‘"Gifting"’ of knowledge that causes the mind to be warped in some way. For a minor transgression such as invoking the Name of Yug Sothoth without the intent of calling his attention the mortal may be ‘"gifted"’ the knowledge of how a particular torture feels, such as the pain of boiling oil spilled upon the hand, leaving no physical mark, and pain swiftly fading. For a more serious transgression such as the betrayal of the Cult to their enemies for personal benefit: the sum total personal knowledge of all torture victims from all places, and all times, may be gifted, swiftly reducing the mortal to a mindless husk. Notable is that most of the time if for example the third tenet was broken to uphold the second, or the second broken to uphold the first then reward may in fact be given.

\begin{center}{\bf Sacrifice}\end{center}

To please the often inscrutable Yog Sothoth requires sacrifice. This comes in many forms ranging from the sacrifice of self into eternal servitude (chancing the complete loss of self), the payment of blood for attention, or the ritual slaying of others for the Lurker at the Threshold. 

\begin{center}{\bf Rewards}\end{center}

As the knower of all things, when one does manage to gain the attention of Yug-Sothoth and also please him the rewards generally involve knowledge squirming permanently into the mind, never to be forgotten, and if the knowledge is sufficient to overcome the mind then the insanity that results is simply the just result of delving too far.  The bloody prayers may gain one insight as to where one should go tomorrow to avoid disaster, while the rituals may grant knowledge never before learned, or forgotten thousands of years past, that may be used to great effect in the present.  Instances of ‘"Forgotten"’ knowledge ranging from the forging of Damascus steel, how to enact teleportation, to the knowledge of a long lost martial technique could be rewards gifted in payment for great sacrifice.

\begin{center}{\bf Identification}\end{center}

There have been rumors that some members who have completed certain rites to the satisfaction of their patron are gifted a means of identifying themselves to other members, oddly even those who have never been taught the method previously, seem to simply recognize it without fail. Though attempts from outsiders to identify this method seem to always result in diversion or outright insanity.  










%\begin{members}
%	\member{\cRasputin{}} 
%	\member{\cPlead{}} 
%	\member{\cPilot{}} 
%
%\end{members}

\end{document}
