\documentclass[greennotebook]{Pestilence} %% [notebook] or [greennotebook]
\begin{document}

\startnotebook{\nApprenticeLab{}}

\begin{page}{first}

They call your \cElder{\parent} a genius and a miracle worker. Soon they will use those words to describe you. You've never been formally introduced to magic, but you know well enough about the spirit world from other elders and shamans from your travels. Different religions with different trappings perhaps, but similar principles. But first, you must refresh your memory of the local magic.

Observe three feats of magic. As much as you hate to admit, your \cElder{\parent} or \cRebel{\sibling} might be able to demonstrate some minor tricks for you. Once done, go to page \nbref{second}

\end{page}

\begin{page}{second}

These feats boggle your mind. The spirit world is difficult to comprehend with the waking mind; perhaps that is why your old research failed so often. The sleeping mind is far more prone to suggestions. Ah, to sleep, perchance to dream. Despite what the pretentious doctor seems to think, there are people in town who read Western literature. It's unfortunate that you can't sleep soundly in the current circumstances. You'll have to rely on some more...err...percussive methods.

Get knocked out by a trusted person. After you wake up, go to page \nbref{third}.

\end{page}

\begin{page}{third}

You were so close. You could almost see brilliant red of the earth's core. You reached to touch it, but the moment you extended your hand, the vision shifted and turned into that of \cOutsider{}, glaring stubbornly at you. What on Earth is \cOutsider{\they} doing in your vision? Could the outsider doctor know more about spiritual practices than \cOutsider{\they} lets on? Earth forbid, is \cOutsider{\they} a spy? Your family does have some enemies from old; you have heard rumors that your \cElder{\parent} forcibly ousted the previous elder from power. If the doctor is truly working for an old enemy, your mission to undermine that wretched snake has become even more pressing than ever.

Start a fight (verbal or physical) with \cOutsider{}. Once you've done so, open page \nbref{fourth}. 

If \cOutsider{} is dead, simply continue with the notebook. This is an issue no longer.

\end{page}

\begin{page}{fourth}

That was a rather uncharacteristic outburst of you. You are a little ashamed of wandering from your task so eagerly. Whatever you learned or did not learn, it's not an essential part of your mission. You need to focus your mind. 

Perhaps you were aware of your next task and wanted to delay it as long as possible. If sleep does not work, death is the next step. You don't wish to cross the line entirely, but you must be close. To know the ways of spirits, you must let go of your body.

Find a way to reach CR 0 or less. You've never been good friends with alcohol, so perhaps that will help you. Failing that, there must be some disgusting concoction you can mess your body with. Just make sure not to get too poisoned. Once you're done, turn to page \nbref{fifth}.

\end{page}

\begin{page}{fifth}

Yes, yes! For the first time in your life, you hear their voices. They speak through the din in your ears. They guide your failing limbs, and though the world blurs, the clouds in your vision begin to form a peculiar shape. Something is close.

Get the True Sight ability card from the GM. You feel your new powers already, but you need proof before you can believe. Use your new ability to detect a creature that cannot be seen through normal eyes. 

If someone is dead, you could try and find their ghost. On the other hand, your new senses strongly suggest the presence of an earth spirit, a shabnak-adyr, within the shelter. If you can dislodge it from whatever it is bound to, you might be able to perceive its true self. A shabnak-adyr's body is made from clay; destroying it is no more heinous than breaking a vase. You just need to be certain you are attacking a shabnak-adyr.

Once you've used True Sight, go to page \nbref{sixth}.

\end{page}

\begin{page}{sixth}

You can see it, but you cannot capture it. To capture it, you must become its kin. You must breed its children within your body and feel its pain as your own. A healer must first be wounded.

Get infected. You may skip this step if you are already infected. Once you are sick, turn to page \nbref{seventh}.

\end{page}

\begin{page}{seventh}

It's done. Your body is wretched and destroyed, but it's done. You understand the spirits now. You are as great as your \cElder{\parent}, perhaps even greater. If only \cElder{\they} had taught you their secrets, if only \cElder{\they} had trusted you, you wouldn't feel the searing heat and stabbing pains throughout your body. It does not matter now. You will cure yourself somehow and contain the plague. You are doing good work. You need no one else. 

Get the Entrapment ability card from the GM. Willpower holds up what your bones cannot. Your CR and gamma score increase by 1.

\end{page}

\endnotebook

\end{document}
