\documentclass[greennotebook]{guildcamp4} %% [notebook] or [greennotebook]
\begin{document}

\startnotebook{\nCbadNotebook{}}

\begin{page}{first}

Another day, another credit. Except this time you get to baby-sit not just one, but {\bf two} clueless idiots.

Talk to \cCgood{}, get \cCgood{his} backstory, and ask \cCgood{his} opinions of the police force so far. Then open page \nbref{second}.

\end{page}

\begin{page}{second}

You know that \cPilot{} is on parole, but not much else. It's always a good idea to get dirt on those around you.

Ask \cPilot{} about \cPilot{his} situation, \cPilot{his} backstory, and the crime for which he was convicted. Then open page \nbref{third}.

\end{page}

\begin{page}{third}

One of the few things you like about this job is getting to play with guns. Arm yourself from the weapons locker aboard the \emph{Anodyne}.

Once docking has been completed, open page \nbref{fourth}.

\end{page}

\begin{page}{fourth}

Ver ships always creep you out. But you should look busy. Look around and meet the crew. Record things like a good police officer would.

Once you've created at least one recording, open page \nbref{fifth}.

Once you've spoken to a Ver for at least two minutes, open page \nbref{sixth}.

\end{page}

\begin{page}{fifth}

To really sell this whole ``legitimate cop" schtick, you should upload a recording into evidence, preferably while someone can see you. 

Upload at least one recording using the terminal aboard the \emph {Anodyne}. Then open page \nbref{seventh}.

\end{page}

\begin{page}{sixth}

Hmm, it's weird that there are humans aboard a Ver ship. You should act concerned.

Talk to at least three humans (or ghouls) for at least two minutes each, then open page \nbref{eighth}.

\end{page}

\begin{page}{seventh}

That reminds you, it would look pretty bad if there were too much evidence of illegal activity on board \emph{TIS Chivalry}. The ship could get impounded, losing you a source of income.

Interrupt \cCgood{} while \cCgood{he} is either recording or uploading. Make it look like an accident. Then open page \nbref{eighth}.

\end{page}

\begin{page}{eighth}

It's time to take care of business.

If you haven't already, talk to \cVone{} about your payment. Once you've done so, open page \nbref{ninth}.

\end{page}

\begin{page}{ninth}

Even if you manage to get paid, you're going to need more credits than {\bf that} to get both the anonymous monkey off your back {\bf and} your old clutchmate out of lockup. Maybe you can find some other sources of income on board.

Hack a terminal on \emph{TIS Chivalry}. Once you've done so, open page \nbref{tenth}.

\end{page}

\begin{page}{tenth}

Find anything useful? If not, maybe you should try some of the other terminals. Or, start shaking down everyone on board to collect enough credits to meet your goals.

If you have at least 2500 credits, open page \nbref{eleventh}.

\end{page}

\begin{page}{eleventh}

Congratulations, officer! It started out looking like a pretty crappy day, but you've actually managed to save up enough credits to get rid of the two biggest thorns in your side. Now you just need to make it out of here alive.

Your desire to get out with the goods grants you +1 CR (both offensive and defensive) for the rest of the game.

\end{page}

\endnotebook

\end{document}
