\documentclass[greennotebook]{guildcamp4} %% [notebook] or [greennotebook]
\begin{document}

\startnotebook{\nCgoodNotebook{}}

\begin{page}{first}

You've finally graduated from the Academy and been handed your first assignment: border patrol! Today is your first day, and you've been looking forward to it your whole life. You made sure to get a full's night's rest, your boots are shined, and your uniform is pressed. You're eager to learn everything you can about how to be the best police officer you can!

Talk to \cCbad{}, get \cCbad{his} backstory, and ask for \cCbad{his} advice on how to be a great police officer. Then open page \nbref{second}.

\end{page}

\begin{page}{second}

This being your first day on the job, you're not sure why there's an ex-con piloting your ship. 

Ask \cPilot{} about \cPilot{his} situation, \cPilot{his} backstory, and the crime for which he was convicted. Then open page \nbref{third}.

\end{page}

\begin{page}{third}

It's always a good idea to be prepared. Arm yourself from the weapons locker aboard the \emph{Anodyne}.

Once docking has been completed, open page \nbref{fourth}.

\end{page}

\begin{page}{fourth}

You've never been on a Veran ship before. Look around and question the crew. If you happen to come across illegal objects or activities, be sure to record them.

Question at least three crew about the ship and their activities for at least two minutes each, then open page \nbref{fifth}.

\end{page}

\begin{page}{fifth}

You've only read about evidence terminals, and never actually used one. But the best way to learn is by doing!

Create at least one recording and upload at least one recording using the terminal aboard the \emph {Anodyne}. Then open page \nbref{sixth}.

\end{page}

\begin{page}{sixth}

Something's not quite right on this ship. Alarm bells are going off in your head. But you can't quite prove anything yet. You need more evidence.

Also, tensions feel...strained. It seems like combat might break out at any time. Your duty as a police officer is to prevent anyone from getting hurt.

If you've uploaded enough evidence for one of the evidence types to read "Proof of...", open page \nbref{seventh}.
If you see any kind of combat, try to stop it, even if it means getting injured. Once you've tried to stop a combat, open page \nbref{eighth}.

\end{page}

\begin{page}{seventh}

The Devil is angry with you for working to prevent sin! You receive a vision of the Devil and his angels tormenting you! This vision will be in effect for ten minutes. Roleplay accordingly. When the ten minutes are up, open page \nbref{eighth}.

\end{page}

\begin{page}{eighth}

At last, the Devil and his angels have left you! There is so much evil aboard the ship! You must cleanse it before any saint would show their face here.

Take holy water to six different rooms aboard TIS Chivalry and say a prayer in each. Rip up each holy water item card as you bless each room. You will need to have at least 6 holy waters to complete this task. When you are done, open page \nbref{ninth}.

\end{page}

\begin{page}{ninth}

If you do not have a remaining holy water, go make one now, because you will need it to confirm the identity of the entity that should appear to you. When you have at least one holy water, open page \nbref{tenth}.

\end{page}

\begin{page}{tenth}

The glowing vision of Saint Michael appears to you! You feel overwhelmed by feelings of love and righteous fervor washing over you. At first you don't think of it, but then you pull out your holy water and say "I sanctify this place in the name of the Father, and of the Son, and of the Holy Ghost." The vision does not flee, but stays there, smiling at you. In your head, you hear the words, "You have done well in this place of cleansing," and then St. Michael fades from view. 

You are in purgatory, and heaven will one day be your reward!

Your CR is +1 for the next ten minutes.

At 15 minutes from end of game (or immediately if there are less than 15 minutes left in game), turn to and open page \nbref{eleventh}.

\end{page}

\begin{page}{eleventh}

You hear a chorus of angels singing and a bright white light from above shines on you! Your very skin glows from the inside out!

Put on a blue headband and explain to nearby people (out of game) what they see and hear. Do this for one minute. During this time you are immune to all attacks.

In a blinding flash you disappear as you are taken bodily into Heaven!

\end{page}

\endnotebook

\end{document}
