\documentclass[greennotebook]{guildcamp4} %% [notebook] or [greennotebook]
\begin{document}

\startnotebook{\nJamesVerBlood{}}

\begin{page}{first}

When you have finished your first research notebook to repair your equipment, you may open page \nbref{second}.

\end{page}

\begin{page}{second}

Great! Now you can finish your research on creating artificial Ver blood! First you'll want to jog your creativity. Go talk to two people about science for two minutes each, then open page \nbref{third}.

\end{page}

\begin{page}{third}

You feel inspired! Now you know that you want to do some control tests on ghoul blood.

Collect blood from two ghouls. You may take blood from yourself to count for one of these samples. Then open page \nbref{fourth}.

\end{page}

\begin{page}{fourth}

You are particularly interested in the red blood cells of ghoul blood. First, go to your \sCentrifuge{} and hold each sample to it for an interruptible 10-count to represent using it on the sample.

Within one minute, hold your \iMicroscope{} up to each sample for an interruptible 5-count to examine the blood cells. Start  at the top of this page again for one or two samples if you can't manage to examine a sample (or both) within one minute. Destroy the sample item cards when you are done. Then open page \nbref{fifth}.

\end{page}

\begin{page}{fifth}

Now you know that you need to do some tests on Ver blood.

Collect blood from two different Ver, then open page \nbref{sixth}.

\end{page}

\begin{page}{sixth}

You are particularly interested in the red blood cells of Ver blood. First, go to your \sCentrifuge{} and hold each sample to it for an interruptible 10-count to represent using it on the sample.

Within one minute, hold your \iMicroscope{} up to each sample for an interruptible 5-count to examine the blood cells. Start  at the top of this page again for one or two samples if you can't manage to examine a sample (or both) within one minute. Destroy the sample item cards when you are done. Then open page \nbref{seventh}.

\end{page}

\begin{page}{seventh}

Your tests have made things much more clear to you! You now know that you need to get ahold of a \iIsotope{}. You know that there is a locked box somewhere on the ship filled with \iIsotope{}s, but you may need some help to get some.

When you have at least one \iIsotope{}, open page \nbref{eighth}.

\end{page}

\begin{page}{eighth}

Yes! You suspect you know how to make artificial Ver blood. Now you only have to test out your hypothesis.

You need a labeled source of electricity, a \iIsotope{}, and a \iTestTube{} of human or ghoul blood. Combine these things in one place for an interruptible 10-count to represent applying electricity to the blood and allowing the blood to be in the presence of the \iIsotope{}. Then open page \nbref{ninth}.

\end{page}

\begin{page}{ninth}

It worked! You may now cross out the item name on the \iTestTube{} of blood and write "Artificial Ver blood." Drinking it will have the same effect as drinking real Ver blood.

You can now use this same process to create as much artificial Ver blood as you'd like. You may also verbally pass on the instructions for how to make artificial Ver blood to anyone you trust.

\end{page}

\endnotebook

\end{document}
