\documentclass[greennotebook]{guildcamp4} %% [notebook] or [greennotebook]
\begin{document}

\startnotebook{\nJoanBooklet{}}

\begin{page}{first}

For centuries you have believed that you are serving your just punishment in Hell, but your recent vision of the Archangel St. Michael has brought this into question. You believe that you may be able to determine whether this vision was a hellish trick or a true vision. If you encounter a similar vision, you believe that if you present it with holy water blessed in the name of the Lord, it will reveal its true nature.

Make holy water, and then open page \nbref{second}.

\end{page}

\begin{page}{second}

You have successfully made holy water, but you don't know when or if you'll have another similar vision to test. But perhaps there are ways to make it more likely for such a vision to occur. Perhaps you have to prove that you deserve to receive such a vision.

First, chastise three people you observe doing something sinful. Then open page \nbref{third}.

\end{page}

\begin{page}{third}

You hear a garbled voice come from nowhere. You can't make out much except for the words "good works." It is gone before you can take out your holy water, but you feel a brief sense of peace fall over you. Your mind feels like it is drifting away in the clouds. Until you turn to the next page, you cannot attack or assist others in martial combat, though you can defend.

Find and assist someone in something you consider a good work, then open page \nbref{fourth}.

\end{page}

\begin{page}{fourth}

The peaceful drifting sensation leaves you, and you haven't had any more visions of the saints. Perhaps you need to do some good works of your own.

Do three different good works (you cannot repeat the same good work), then open page \nbref{fifth}.

\end{page}

\begin{page}{fifth}

You still haven't had any more visions or heard any more voices, so it occurs to you that the sins and lack of faith of others may be at fault.

Talk to three different people for two minutes each about your religious beliefs, such as morals, sin and good works, heaven, hell, purgatory, saints, and God. Then open page \nbref{sixth}.

\end{page}

\begin{page}{sixth}

You notice that for the most part, the people you spoke with did not seem open to your belief system. Perhaps it is up to you to prevent them from sinning and tainting the environment around you.

Stop two different interruptible mechanics you see people performing that you consider a sin. Then open page \nbref{seventh}.

\end{page}

\begin{page}{seventh}

The Devil is angry with you for working to prevent sin! You receive a vision of the Devil and his angels tormenting you! (All others are seen and heard as if they are such.) This vision will be in effect for ten minutes. Roleplay accordingly. When the ten minutes are up, open page \nbref{eighth}.

\end{page}

\begin{page}{eighth}

At last, the Devil and his angels have left you! There is so much evil aboard the ship! You must cleanse it before any saint would show their face here.

Take holy water to six different rooms aboard TIS Chivalry and say a prayer in each. Rip up each holy water item card as you bless each room. You will need to have at least 6 holy waters to complete this task. When you are done, open page \nbref{ninth}.

\end{page}

\begin{page}{ninth}

If you do not have a remaining holy water, go make one now, because you will need it to confirm the identity of the entity that should appear to you. When you have at least one holy water, open page \nbref{tenth}.

\end{page}

\begin{page}{tenth}

The glowing vision of Saint Michael appears to you! You feel overwhelmed by feelings of love and righteous fervor washing over you. At first you don't think of it, but then you pull out your holy water and say "I sanctify this place in the name of the Father, and of the Son, and of the Holy Ghost." The vision does not flee, but stays there, smiling at you. In your head, you hear the words, "You have done well in this place of cleansing," and then St. Michael fades from view. 

You are in purgatory, and heaven will one day be your reward! Your CR is +1 for the next ten minutes.

You want to do all you can to increase your religious fervor!

During the last 15 minutes from end of game, turn to and open page \nbref{eleventh} if your fervor is at least 6.

\end{page}

\begin{page}{eleventh}

You hear a chorus of angels singing and a bright white light from above shines on you! Your very skin glows from the inside out!

Put on a blue headband and explain to nearby people (out of game) what they see and hear. Do this for one minute. During this time you are immune to all attacks.

In a blinding flash you disappear as you are taken bodily into Heaven!

\end{page}

\endnotebook

\end{document}
