
%%%%
%%
%% This file sets up the Sign and Label datatypes and creates Sign and
%% Label macros.
%%
%% Signs generally represent interesting parts of game area, usually
%% as things posted on walls.  Labels represent other things, often on
%% or inside envelopes, that are part of complex mechanics.
%%
%% The default value for \MYloc will inherit location from the Place
%% or Sign most immediately up the ownership tree.  Override this by
%% setting \MYloc to anything (even blank).
%%
%% Sign is for full-sized signs that would cover most of a large
%% manila envelope; SignMedium is for signs sized to half-sized manila
%% envelopes; SignSmall is for signs sized for small manila envelopes
%% (the same size as item cards).  Label, LabelMedium, and LabelSmall
%% are analagous, but they don't have a \takedownby note at the
%% bottom.  You can always use a sign or label without an envelope or
%% with a differently-sized envelope.  Choose which based on
%% visibility and content.
%%
%% SignTiny is for signs you want to be hard to find; it is small and
%% does not have a \takedownby note.  SignDot is for a very small
%% "dot" which only has a title.
%%
%% SignStrip produces a strip of paper (without a \takedownby note)
%% with labels on the outside that show on both sides if you fold it
%% in half.  These are a convenient alternative to sub-envelopes. They
%% can also be used for "s-packets" taped to walls (see
%% Extras/README-s-packets).
%%
%% LabelCover produces a label similar to the cover to a research
%% notebook.  LabelPage, likewise, produces a page.
%%
%% EOG is for full-sized end-of-game signs.
%%
%%%%%

\DECLARESUBTYPE{Sign}{Element}
\PRESETS{Sign}{
  \FD\MYloc	{\mylocation}	%% real-space location
  \FD\MYtext	{} 			%% text of sign
I  }
\POSTSETS{Sign}{
  \edef\mylocation{\MYloc}
  \protected@edef\@ownerstring{%
    \MYname%
    \ifx\mylocation\empty\else\ (\mylocation)\fi%
    }
  }
\def\mylocation{}

\def\loc#1{\rs\MYloc{#1}}

\DECLARESUBTYPE{SignMedium}{Sign}
\DECLARESUBTYPE{SignSmall}{Sign}
\DECLARESUBTYPE{SignTiny}{Sign}
\DECLARESUBTYPE{SignDot}{Sign}
\PRESETS{SignDot}{\s\MYtext{}}

\DECLARESUBTYPE{Label}{Sign}
\PRESETS{Label}{\s\MYloc{}}
\DECLARESUBTYPE{LabelMedium}{Label}
\DECLARESUBTYPE{LabelSmall}{Label}

\DECLARESUBTYPE{SignStrip}{Sign}
\DECLARESUBTYPE{LabelCover}{Label}
\DECLARESUBTYPE{LabelPage}{Label}

\DECLARESUBTYPE{EOG}{Sign}
\PRESETS{EOG}{%
  \s\MYname	{End Of Game}
  \s\MYtext	{{\bf\Huge You may not pass through here.}}
  }


%%%%%
%% \signbig[<location>]{<name>}{<text>}
%% \eog[<location>]
%%
%% \signmdeium[<location>]{<name>}{<text>}
%% \signsmall[<location>]{<name>}{<text>}
%% \signtiny[<location>]{<name>}{<text>}
%% \signdot[<location>]{<name>}
%%
%% \labelbig{<name>}{<text>}
%% \labelmedium{<name>}{<text>}
%% \labelsmall{<name>}{<text>}
%%
%% \signstrip[<location>]{<name>}{<text>}
%% \labelcover{<name>}{<text>}
%% \labelpage{<name>}{<text>}
\newinstance{Sign}{\signbig[3][\mylocation]}{
  \s\MYloc{#1}\s\MYname{#2}\s\MYtext{#3}}
\newinstance{EOG}{\eog[1][\mylocation]}{\s\MYloc{#1}}

\newinstance{SignMedium}{\signmedium[3][\mylocation]}{
  \s\MYloc{#1}\s\MYname{#2}\s\MYtext{#3}}
\newinstance{SignSmall}{\signsmall[3][\mylocation]}{
  \s\MYloc{#1}\s\MYname{#2}\s\MYtext{#3}}
\newinstance{SignTiny}{\signtiny[3][\mylocation]}{
  \s\MYloc{#1}\s\MYname{#2}\s\MYtext{#3}}
\newinstance{SignDot}{\signdot[2][\mylocation]}{
  \s\MYloc{#1}\s\MYname{#2}}

\newinstance{Label}{\labelbig[2]}{
  \s\MYname{#1}\s\MYtext{#2}}
\newinstance{LabelMedium}{\labelmedium[2]}{
  \s\MYname{#1}\s\MYtext{#2}}
\newinstance{LabelSmall}{\labelsmall[2]}{
  \s\MYname{#1}\s\MYtext{#2}}

\newinstance{SignStrip}{\signstrip[3][\mylocation]}{
  \s\MYloc{#1}\s\MYname{#2}\s\MYtext{#3}}
\newinstance{LabelCover}{\labelcover[2]}{
  \s\MYname{#1}\s\MYtext{#2}}
\newinstance{LabelPage}{\labelpage[2]}{
  \s\MYname{#1}\s\MYtext{#2}}


%%%%%
%% \sEOG{}
%% use \sEOg[\loc{<location>}]{} for EOG sign at a specific place
\NEW{EOG}{\sEOG}{
  }


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\NEW{Sign}{\sTest}{
  \s\MYname	{A Room}
  \s\MYloc	{10-250}
  \s\MYtext	{A lecture hall with large, sliding blackboards.}
  }

\NEW{Sign}{\sGFG}{
	\s\MYname	{X Packet}
	\s\MYloc	{}
	\s\MYtext	{This is an Out of Game Packet for retrieval of relevant things}
	\s\MYitems {\multi{3}{\iSerum{}}}
}

\NEW{Sign}{\sBridgeC}{
	\s\MYname	{The Bridge of the Chivalry}
	\s\MYloc	{}
	\s\MYtext	{A room with several consoles that detail the status of the ship}
}


\NEW{Sign}{\sComArrayCLoggedIn}{
	\s\MYname	{Communications Array Terminal (Logged In)}
	\s\MYloc	{}
	\s\MYtext	{Within are several files. Of particular note is a record of how high of an ALERT LEVEL was reached}
}

\NEW{Sign}{\sComArrayCLoggedOut}{
	\s\MYname	{Communications Array Terminal (Logged Out)}
	\s\MYloc	{}
	\s\MYtext	{A monitor, a keyboard, and a dock for connecting portable devices. Within are all recorded external communications, such as ALERT LEVEL. If you are an officer of the \emph{Chivalry}, you may read the next sheet without hacking. Hacking Difficulty 3 }
}

\NEW{Sign}{\sComArrayALoggedIn}{
	\s\MYname	{Communications Array Terminal (Logged In)}
	\s\MYloc	{}
	\s\MYtext	{Within are several files. Of particular note is a record of how high of an ALERT LEVEL was reached}
}

\NEW{Sign}{\sComArrayALoggedOut}{
	\s\MYname	{Communications Array Terminal (Logged Out)}
	\s\MYloc	{}
	\s\MYtext	{A monitor, a keyboard, and a dock for connecting portable devices. Within are all recorded external communications, such as ALERT LEVEL. If you are an officer of the \emph{Anodyne}, you may read the next sheet without hacking. Hacking Difficulty 3}
}

\NEW{Sign}{\sCrewQ}{
	\s\MYname	{Crew Quarters}
	\s\MYloc	{}
	\s\MYtext	{Quarters for the Officers and Crew}
}

\NEW{Sign}{\sEngineC}{
	\s\MYname	{The Engine Room of the Chivalry}
	\s\MYloc	{}
	\s\MYtext	{A room with several consoles that detail the status of the ship's engine}
}

\NEW{Sign}{\sStealth}{
	\s\MYname	{Stealth Suite}
	\s\MYloc	{}
	\s\MYtext	{This is the cloaking device for the Chivalry}
}

\NEW{Sign}{\sStealthTerminalLoggedIn}{
	\s\MYname	{Computer Terminal for the Chivalry Stealth Suite (Logged In)}
	\s\MYloc	{}
	\s\MYtext	{Within are several files. Of note is the frequency manipulations required to maintain stealth. You may copy this by spending 1 minute accessing this terminal, followed by removing an item from the packet underneath this sign. The item is infinite in supply, if it is out please ask a GM.}
	\s\MYitems {\multi{5}{\iStealthTech{}}}
}

\NEW{Sign}{\sStealthTerminalLoggedOut}{
	\s\MYname	{Computer Terminal for the Chivalry Stealth Suite (Logged Out)}
	\s\MYloc	{}
	\s\MYtext	{A monitor, a keyboard, and a dock for connecting portable devices. If you are an officer of the \emph{Chivalry}, you can read the next sheet without hacking. Hacking Difficulty 3}
}

\NEW{Sign}{\sFount}{
	\s\MYname	{Water Faucet}
	\s\MYloc	{}
	\s\MYtext	{A faucet from which clean water can be obtained with a \iTestTube{}. Hold the \iTestTube{} to the faucet for a 5 count.}
}

\NEW{Sign}{\sStationFourFixed}{
	\s\MYname	{Operational Engine}
	\s\MYloc	{}
	\s\MYtext	{This device powers the Chivalry, allowing the captain to control its speed and direction. The engine is running smoothly.  You may not interact with this station unless you know otherwise.}
}

\NEW{Sign}{\sStationFourDiagnosed}{
	\s\MYname	{Damaged Engine}
	\s\MYloc	{}
	\s\MYtext	{This device powers the Chivalry, allowing the captain to control its speed and direction.  Sparking dangerously the engine seems to be about to fail completely. You may not interact with this station unless you know otherwise. Upon diagnosing the problem you see that you need to find a \iCircuitBoard{}. Install the \iCircuitBoard{} by staying within one ZOC of the sign for 5 minutes with the help two other people.}
}

\NEW{Sign}{\sStationFourBroken}{
	\s\MYname	{Damaged Engine}
	\s\MYloc	{}
	\s\MYtext	{This device powers the Chivalry, allowing the captain to control its speed and direction.  Sparking dangerously the engine seems to be about to fail completely. You may not interact with this station unless you know otherwise. If you have the Repair ability you may lift this sign and read the one below it.}
}

\NEW{Sign}{\sStationFourRunning}{
	\s\MYname	{Engine}
	\s\MYloc	{}
	\s\MYtext	{This device powers the Chivalry, allowing the captain to control its speed and direction.  The engine is running smoothly. At T+2 Hrs remove this sign.  }
}

\NEW{Sign}{\sPillage}{
	\s\MYname	{The Pillage}
	\s\MYloc	{}
	\s\MYtext	{A room with several consoles that detail the status of the ship}
}

\NEW{Sign}{\sEngineP}{
	\s\MYname	{The Engine of the Pillage}
	\s\MYloc	{}
	\s\MYtext	{An engine with several consoles that detail the status of the ship's engine}
}

\NEW{Sign}{\sControlP}{
	\s\MYname	{Control Panel}
	\s\MYloc	{}
	\s\MYtext	{Controls for the Pillage, if you are a Veran Officer you have permission to use these, Otherwise you need the \iCaptainRing{} for override.}
}

\NEW{Sign}{\sRaid}{
	\s\MYname	{The Raid}
	\s\MYloc	{}
	\s\MYtext	{A room with several consoles that detail the status of the ship's engine}
}

\NEW{Sign}{\sEngineR}{
	\s\MYname	{The Engine of the Raid}
	\s\MYloc	{}
	\s\MYtext	{an Engine with several consoles that detail the status of the ship's engine}
}


\NEW{Sign}{\sControlR}{
	\s\MYname	{Control Panel}
	\s\MYloc	{}
	\s\MYtext	{Controls for the Raid. If you are a Veran Officer you have permission to use these, Otherwise you need the \iCaptainRing{} for override.}
}

\NEW{Sign}{\sStationPFixed}{
	\s\MYname	{Operational Engine}
	\s\MYloc	{}
	\s\MYtext	{This device powers the Pillage, allowing the captain to control its speed and direction. The engine is running smoothly.  You may not interact with this station unless you know otherwise.}
}

\NEW{Sign}{\sStationPDiagnosed}{
	\s\MYname	{Damaged Engine}
	\s\MYloc	{}
	\s\MYtext	{This device powers the Pillage, allowing the captain to control its speed and direction.  Sparking dangerously the engine seems to be about to fail completely. You may not interact with this station unless you know otherwise. Upon diagnosing the problem you see that you need to find a \iCircuitBoard{}. Install the \iCircuitBoard{} by staying within one ZOC of the sign for 5 minutes with the help two other people.}
}

\NEW{Sign}{\sStationPBroken}{
	\s\MYname	{Damaged Engine}
	\s\MYloc	{}
	\s\MYtext	{This device powers the Pillage, allowing the captain to control its speed and direction.  Sparking dangerously the engine seems to be about to fail completely. You may not interact with this station unless you know otherwise. If you have the Repair ability you may lift this sign and read the one below it.}
}

\NEW{Sign}{\sStationPRunning}{
	\s\MYname	{Engine}
	\s\MYloc	{}
	\s\MYtext	{This device powers the Pillage, allowing the captain to control its speed and direction.  The engine is running smoothly.   }
}

\NEW{Sign}{\sStationRFixed}{
	\s\MYname	{Operational Engine}
	\s\MYloc	{}
	\s\MYtext	{This device powers the Raid, allowing the captain to control its speed and direction. The engine is running smoothly.  You may not interact with this station unless you know otherwise.}
}

\NEW{Sign}{\sStationRDiagnosed}{
	\s\MYname	{Damaged Engine}
	\s\MYloc	{}
	\s\MYtext	{This device powers the Raid, allowing the captain to control its speed and direction.  Sparking dangerously the engine seems to be about to fail completely. You may not interact with this station unless you know otherwise. Upon diagnosing the problem you see that you need to find a \iCircuitBoard{}. Install the \iCircuitBoard{} by staying within one ZOC of the sign for 5 minutes with the help two other people.}
}

\NEW{Sign}{\sStationRBroken}{
	\s\MYname	{Damaged Engine}
	\s\MYloc	{}
	\s\MYtext	{This device powers the Raid, allowing the captain to control its speed and direction.  Sparking dangerously the engine seems to be about to fail completely. You may not interact with this station unless you know otherwise. If you have the Repair ability you may lift this sign and read the one below it.}
}

\NEW{Sign}{\sStationRRunning}{
	\s\MYname	{Engine}
	\s\MYloc	{}
	\s\MYtext	{This device powers the Raid, allowing the captain to control its speed and direction.  The engine is running smoothly.   }
}

\NEW{Sign}{\sBioLab}{
	\s\MYname	{The Biological Laboratory}
	\s\MYloc	{}
	\s\MYtext	{A room full of bits of technological components and tools all seemingly geared toward dealing with blood in some way}
}

\NEW{Sign}{\sBloodAnalyzer}{
	\s\MYname	{Blood Analyzer}
	\s\MYloc	{}
	\s\MYtext	{A machine made to analyze blood. In order to analyze the blood you have collected you must insert the blood into the analyzer and conduct a 15 count (note this is interruptible.) 
Upon successful completion destroy the blood item card.}
}

\NEW{Sign}{\sTestTubeRack}{
	\s\MYname	{Rack of Test Tubes}
	\s\MYloc	{}
	\s\MYitems	{\multi{20}{\iTestTube{}}}
	\s\MYtext	{Rack with many TestTubes, You can take ONE ONCE EVERY 30 SEC }
}

\NEW{Sign}{\sBioLabLock}{
	\s\MYname	{Specimen Containment Field}
	\s\MYloc	{}
	\s\MYtext	{The double fields prevent the passage of any living cells and require the activation of the lever to disengage.}
}

\NEW{Sign}{\sBioLabLever}{
	\s\MYname	{Lever for Specimen Containment Field}
	\s\MYloc	{}
	\s\MYtext	{This lever will deactivate the Specimen Containment Field if it comes into contact with the control rod.}
}

\NEW{Sign}{\sBrainDead}{
	\s\MYname	{Stasis Pods}
	\s\MYloc	{}
	\s\MYtext	{Upon looking closer, all of the stasis pods show that the human victims have been rendered brain dead. If you have a Kappa packet, open it.}
	\s\MYnumber	{3284}
}

\NEW{Sign}{\sStasisPods}{
	\s\MYname	{Stasis Pods}
	\s\MYloc	{}
	\s\MYtext	{There is a hidden compartment with hundreds of stasis pods, most containing bodies. To take a closer look, wait with your hand on this sign for two minutes and then lift up this sign.}
	\s\MYnumber	{5333}
}

\NEW{Sign}{\sHiddenWall}{
	\s\MYname	{Chivalry Painting}
	\s\MYloc	{}
	\s\MYtext	{There is a grand painting of the \emph{Chivalry} against the backdrop of a nebula on this wall.}
}

\NEW{SignTiny}{\sBiolockedSwitch}{
	\s\MYname	{Switch with Bio Reader}
	\s\MYloc	{}
	\s\MYtext	{This switch requires the blood of a Ver Officer to activate. If you have are Ver or have some, look underneath this sign.}
}

\NEW{SignTiny}{\sBiolockedSwitchActive}{
	\s\MYname	{Switch with Bio Reader (Activated)}
	\s\MYloc	{}
	\s\MYtext	{Upon activation, the painting on the wall slides aside. You may lift the painting sign and look underneath. Deactivation of the switch puts the painting back into place and requires no blood to trigger.}
}

\NEW{Sign}{\sAnodyne}{
	\s\MYname	{The HMS Anodyne}
	\s\MYloc	{3rd Floor}
	\s\MYtext	{The {\it HMS Anodyne}, a small Frith police cruiser.}
}

\NEW{Sign}{\sAnodyneScan}{
	\s\MYname	{Ship Scanner}
	\s\MYloc	{}
	\s\MYtext	{Prototype Scanners using cutting edge technology}
}

\NEW{Sign}{\sScanTerminalLoggedIn}{
	\s\MYname	{Computer Terminal for Anodyne Ship Scanner (Logged In)}
	\s\MYloc	{}
	\s\MYtext	{Within are several files. Of particular note is a program with a special algorithm for attmepting to find stealthed ships. You may copy this by spending 1 minute accessing this terminal, followed by removing an item from the packet underneath this sign. The item is infinite in supply, if it is out please ask a GM. }
	\s\MYitems {\multi{5}{\iScanTech{}}}
}

\NEW{Sign}{\sScanTerminalLoggedOut}{
	\s\MYname	{Computer Terminal for Anodyne Ship Scanner (Logged Out)}
	\s\MYloc	{}
	\s\MYtext	{A monitor, a keyboard, and a dock for connecting portable devices. If you are an officer of the \emph{Anodyne}, you can read the next sheet without hacking. Hacking Difficulty 3}
}


\NEW{Sign}{\sAnodyneTerminalLoggedOut}{
	\s\MYname	{Computer Terminal for Uploading Evidence (Logged Out)}
	\s\MYloc	{}
	\s\MYtext	{A monitor, a keyboard, and a dock for connecting portable devices. If you are an officer of the \emph{Anodyne}, you can read the next sheet without hacking. Hacking Difficulty 3}
}

\NEW{Label}{\sAnodyneTerminalOne}{
    \s\MYname   {Evidence Terminal 1/8}
    \s\MYloc    {}
    \s\MYtext   {When uploading evidence, consult this table to determine the evidence type, then place the recording in the corresponding small envelope (behind these sheets). Unless you know otherwise, try not to look at rows other than the one you're uploading.

        \centering
        \begin{tabular}{|c|c||c|}
        \hline
        \bf A/I/S & \bf C & \bf E \\
        \hline
0000& &5\\ 0000&24873&5\\ 0000&31479&5\\ 0000&34875&5\\ 0000&39875&5\\ 0000&54781&5\\ 0000&64817&5\\ 0000&64825&5\\ 0000&67128&5\\ 0000&69752&5\\ 0000&84785&5\\ 0000&97248&5\\ 0000&97254&5\\ 0029& &5\\ 0029&24873&5\\ 0029&31479&5\\ 0029&34875&5\\ 0029&39875&5\\ 0029&54781&5\\ 0029&64817&5\\ 0029&64825&5\\ 0029&67128&5\\ 0029&69752&5\\ 0029&84785&5\\ 0029&97248&5\\ 0029&97254&5\\ 0063& &5\\ 0063&24873&5\\ 0063&31479&5\\ 0063&34875&5\\ 0063&39875&5\\ 0063&54781&5\\ 0063&64817&5\\ 0063&64825&5\\ 0063&67128&5\\ 0063&69752&5\\ 0063&84785&4\\ 0063&97248&5\\ 0063&97254&5\\ 0067& &5\\ 
        \hline
        \end{tabular}
        \quad
        \begin{tabular}{|c|c||c|}
        \hline
        \bf A/I/S & \bf C & \bf E \\
        \hline
0067&24873&5\\ 0067&31479&5\\ 0067&34875&5\\ 0067&39875&5\\ 0067&54781&5\\ 0067&64817&5\\ 0067&64825&5\\ 0067&67128&5\\ 0067&69752&5\\ 0067&84785&5\\ 0067&97248&5\\ 0067&97254&5\\ 0124& &5\\ 0124&24873&5\\ 0124&31479&5\\ 0124&34875&5\\ 0124&39875&5\\ 0124&54781&5\\ 0124&64817&5\\ 0124&64825&5\\ 0124&67128&5\\ 0124&69752&5\\ 0124&84785&5\\ 0124&97248&5\\ 0124&97254&5\\ 0552& &1\\ 0552&24873&1\\ 0552&31479&6\\ 0552&34875&1\\ 0552&39875&3\\ 0552&54781&1\\ 0552&64817&1\\ 0552&64825&1\\ 0552&67128&1\\ 0552&69752&1\\ 0552&84785&4\\ 0552&97248&1\\ 0552&97254&1\\ 0564& &5\\ 0564&24873&5\\ 
        \hline
        \end{tabular}
        \quad
        \begin{tabular}{|c|c||c|}
        \hline
        \bf A/I/S & \bf C & \bf E \\
        \hline
0564&31479&5\\ 0564&34875&5\\ 0564&39875&5\\ 0564&54781&5\\ 0564&64817&5\\ 0564&64825&5\\ 0564&67128&5\\ 0564&69752&5\\ 0564&84785&5\\ 0564&97248&5\\ 0564&97254&5\\ 0579& &5\\ 0579&24873&5\\ 0579&31479&5\\ 0579&34875&5\\ 0579&39875&5\\ 0579&54781&5\\ 0579&64817&5\\ 0579&64825&5\\ 0579&67128&5\\ 0579&69752&5\\ 0579&84785&5\\ 0579&97248&5\\ 0579&97254&5\\ 0638& &5\\ 0638&24873&5\\ 0638&31479&5\\ 0638&34875&5\\ 0638&39875&5\\ 0638&54781&5\\ 0638&64817&5\\ 0638&64825&5\\ 0638&67128&5\\ 0638&69752&5\\ 0638&84785&5\\ 0638&97248&5\\ 0638&97254&5\\ 1036& &5\\ 1036&24873&5\\ 1036&31479&5\\ 
        \hline
        \end{tabular}
    }
}

\NEW{Label}{\sAnodyneTerminalTwo}{
    \s\MYname   {Evidence Terminal 2/8}
    \s\MYloc    {}
    \s\MYtext   {
        \centering
        \begin{tabular}{|c|c||c|}
        \hline
        \bf A/I/S & \bf C & \bf E \\
        \hline
1036&34875&5\\ 1036&39875&5\\ 1036&54781&5\\ 1036&64817&5\\ 1036&64825&5\\ 1036&67128&5\\ 1036&69752&5\\ 1036&84785&5\\ 1036&97248&5\\ 1036&97254&5\\ 1127& &5\\ 1127&24873&5\\ 1127&31479&5\\ 1127&34875&5\\ 1127&39875&5\\ 1127&54781&5\\ 1127&64817&5\\ 1127&64825&5\\ 1127&67128&5\\ 1127&69752&5\\ 1127&84785&5\\ 1127&97248&5\\ 1127&97254&5\\ 1156& &5\\ 1156&24873&5\\ 1156&31479&5\\ 1156&34875&5\\ 1156&39875&5\\ 1156&54781&5\\ 1156&64817&5\\ 1156&64825&5\\ 1156&67128&5\\ 1156&69752&5\\ 1156&84785&5\\ 1156&97248&5\\ 1156&97254&5\\ 1294& &1\\ 1294&24873&1\\ 1294&31479&6\\ 1294&34875&1\\ 
        \hline
        \end{tabular}
        \quad
        \begin{tabular}{|c|c||c|}
        \hline
        \bf A/I/S & \bf C & \bf E \\
        \hline
1294&39875&3\\ 1294&54781&1\\ 1294&64817&1\\ 1294&64825&1\\ 1294&67128&1\\ 1294&69752&1\\ 1294&84785&4\\ 1294&97248&1\\ 1294&97254&1\\ 1580& &5\\ 1580&24873&5\\ 1580&31479&5\\ 1580&34875&5\\ 1580&39875&5\\ 1580&54781&5\\ 1580&64817&5\\ 1580&64825&5\\ 1580&67128&5\\ 1580&69752&5\\ 1580&84785&5\\ 1580&97248&5\\ 1580&97254&5\\ 1642& &5\\ 1642&24873&5\\ 1642&31479&5\\ 1642&34875&5\\ 1642&39875&5\\ 1642&54781&5\\ 1642&64817&5\\ 1642&64825&5\\ 1642&67128&5\\ 1642&69752&5\\ 1642&84785&5\\ 1642&97248&5\\ 1642&97254&5\\ 2063& &5\\ 2063&24873&5\\ 2063&31479&5\\ 2063&34875&5\\ 2063&39875&5\\ 
        \hline
        \end{tabular}
        \quad
        \begin{tabular}{|c|c||c|}
        \hline
        \bf A/I/S & \bf C & \bf E \\
        \hline
2063&54781&5\\ 2063&64817&5\\ 2063&64825&5\\ 2063&67128&5\\ 2063&69752&5\\ 2063&84785&5\\ 2063&97248&5\\ 2063&97254&5\\ 2137& &5\\ 2137&24873&5\\ 2137&31479&5\\ 2137&34875&5\\ 2137&39875&5\\ 2137&54781&5\\ 2137&64817&5\\ 2137&64825&5\\ 2137&67128&5\\ 2137&69752&5\\ 2137&84785&5\\ 2137&97248&5\\ 2137&97254&5\\ 2142& &5\\ 2142&24873&5\\ 2142&31479&5\\ 2142&34875&5\\ 2142&39875&5\\ 2142&54781&5\\ 2142&64817&5\\ 2142&64825&5\\ 2142&67128&5\\ 2142&69752&5\\ 2142&84785&5\\ 2142&97248&5\\ 2142&97254&5\\ 2574& &5\\ 2574&24873&5\\ 2574&31479&5\\ 2574&34875&5\\ 2574&39875&5\\ 2574&54781&5\\ 
        \hline
        \end{tabular}
    }
}

\NEW{Label}{\sAnodyneTerminalThree}{
    \s\MYname   {Evidence Terminal 3/8}
    \s\MYloc    {}
    \s\MYtext   {
        \centering
        \begin{tabular}{|c|c||c|}
        \hline
        \bf A/I/S & \bf C & \bf E \\
        \hline
2574&64817&5\\ 2574&64825&5\\ 2574&67128&5\\ 2574&69752&5\\ 2574&84785&5\\ 2574&97248&5\\ 2574&97254&5\\ 2626& &5\\ 2626&24873&5\\ 2626&31479&5\\ 2626&34875&5\\ 2626&39875&5\\ 2626&54781&5\\ 2626&64817&5\\ 2626&64825&5\\ 2626&67128&5\\ 2626&69752&5\\ 2626&84785&5\\ 2626&97248&5\\ 2626&97254&5\\ 2632& &5\\ 2632&24873&5\\ 2632&31479&5\\ 2632&34875&5\\ 2632&39875&5\\ 2632&54781&5\\ 2632&64817&5\\ 2632&64825&5\\ 2632&67128&5\\ 2632&69752&5\\ 2632&84785&5\\ 2632&97248&5\\ 2632&97254&5\\ 2647& &5\\ 2647&24873&5\\ 2647&31479&5\\ 2647&34875&5\\ 2647&39875&5\\ 2647&54781&5\\ 2647&64817&5\\ 
        \hline
        \end{tabular}
        \quad
        \begin{tabular}{|c|c||c|}
        \hline
        \bf A/I/S & \bf C & \bf E \\
        \hline
2647&64825&5\\ 2647&67128&5\\ 2647&69752&5\\ 2647&84785&5\\ 2647&97248&5\\ 2647&97254&5\\ 2677& &5\\ 2677&24873&5\\ 2677&31479&5\\ 2677&34875&5\\ 2677&39875&5\\ 2677&54781&5\\ 2677&64817&5\\ 2677&64825&5\\ 2677&67128&5\\ 2677&69752&5\\ 2677&84785&5\\ 2677&97248&5\\ 2677&97254&5\\ 2680& &5\\ 2680&24873&5\\ 2680&31479&5\\ 2680&34875&5\\ 2680&39875&5\\ 2680&54781&5\\ 2680&64817&5\\ 2680&64825&5\\ 2680&67128&5\\ 2680&69752&5\\ 2680&84785&5\\ 2680&97248&5\\ 2680&97254&5\\ 2697& &5\\ 2697&24873&5\\ 2697&31479&5\\ 2697&34875&5\\ 2697&39875&5\\ 2697&54781&5\\ 2697&64817&5\\ 2697&64825&5\\ 
        \hline
        \end{tabular}
        \quad
        \begin{tabular}{|c|c||c|}
        \hline
        \bf A/I/S & \bf C & \bf E \\
        \hline
2697&67128&5\\ 2697&69752&5\\ 2697&84785&5\\ 2697&97248&5\\ 2697&97254&5\\ 3155& &5\\ 3155&24873&5\\ 3155&31479&5\\ 3155&34875&5\\ 3155&39875&5\\ 3155&54781&5\\ 3155&64817&5\\ 3155&64825&5\\ 3155&67128&5\\ 3155&69752&5\\ 3155&84785&5\\ 3155&97248&5\\ 3155&97254&5\\ 3284& &2\\ 3284&24873&2\\ 3284&31479&2\\ 3284&34875&2\\ 3284&39875&2\\ 3284&54781&2\\ 3284&64817&2\\ 3284&64825&2\\ 3284&67128&2\\ 3284&69752&2\\ 3284&84785&2\\ 3284&97248&2\\ 3284&97254&2\\ 3603& &5\\ 3603&24873&5\\ 3603&31479&5\\ 3603&34875&5\\ 3603&39875&5\\ 3603&54781&5\\ 3603&64817&5\\ 3603&64825&5\\ 3603&67128&5\\ 
        \hline
        \end{tabular}
    }
}

\NEW{Label}{\sAnodyneTerminalFour}{
    \s\MYname   {Evidence Terminal 4/8}
    \s\MYloc    {}
    \s\MYtext   {
        \centering
        \begin{tabular}{|c|c||c|}
        \hline
        \bf A/I/S & \bf C & \bf E \\
        \hline
3603&69752&5\\ 3603&84785&5\\ 3603&97248&5\\ 3603&97254&5\\ 3700& &5\\ 3700&24873&5\\ 3700&31479&5\\ 3700&34875&5\\ 3700&39875&5\\ 3700&54781&5\\ 3700&64817&5\\ 3700&64825&5\\ 3700&67128&5\\ 3700&69752&5\\ 3700&84785&5\\ 3700&97248&5\\ 3700&97254&5\\ 4135& &1\\ 4135&24873&1\\ 4135&31479&6\\ 4135&34875&1\\ 4135&39875&3\\ 4135&54781&1\\ 4135&64817&1\\ 4135&64825&1\\ 4135&67128&1\\ 4135&69752&1\\ 4135&84785&4\\ 4135&97248&1\\ 4135&97254&1\\ 4157& &5\\ 4157&24873&5\\ 4157&31479&5\\ 4157&34875&5\\ 4157&39875&5\\ 4157&54781&5\\ 4157&64817&5\\ 4157&64825&5\\ 4157&67128&5\\ 4157&69752&5\\ 
        \hline
        \end{tabular}
        \quad
        \begin{tabular}{|c|c||c|}
        \hline
        \bf A/I/S & \bf C & \bf E \\
        \hline
4157&84785&4\\ 4157&97248&5\\ 4157&97254&5\\ 4229& &5\\ 4229&24873&5\\ 4229&31479&5\\ 4229&34875&5\\ 4229&39875&5\\ 4229&54781&5\\ 4229&64817&5\\ 4229&64825&5\\ 4229&67128&5\\ 4229&69752&5\\ 4229&84785&5\\ 4229&97248&5\\ 4229&97254&5\\ 4650& &1\\ 4650&24873&1\\ 4650&31479&6\\ 4650&34875&1\\ 4650&39875&3\\ 4650&54781&1\\ 4650&64817&1\\ 4650&64825&1\\ 4650&67128&1\\ 4650&69752&1\\ 4650&84785&4\\ 4650&97248&1\\ 4650&97254&1\\ 4719& &5\\ 4719&24873&5\\ 4719&31479&5\\ 4719&34875&5\\ 4719&39875&5\\ 4719&54781&5\\ 4719&64817&5\\ 4719&64825&5\\ 4719&67128&5\\ 4719&69752&5\\ 4719&84785&5\\ 
        \hline
        \end{tabular}
        \quad
        \begin{tabular}{|c|c||c|}
        \hline
        \bf A/I/S & \bf C & \bf E \\
        \hline
4719&97248&5\\ 4719&97254&5\\ 5216& &2\\ 5216&24873&2\\ 5216&31479&2\\ 5216&34875&2\\ 5216&39875&2\\ 5216&54781&2\\ 5216&64817&2\\ 5216&64825&2\\ 5216&67128&2\\ 5216&69752&2\\ 5216&84785&2\\ 5216&97248&2\\ 5216&97254&2\\ 5275& &5\\ 5275&24873&5\\ 5275&31479&5\\ 5275&34875&5\\ 5275&39875&5\\ 5275&54781&5\\ 5275&64817&5\\ 5275&64825&5\\ 5275&67128&5\\ 5275&69752&5\\ 5275&84785&5\\ 5275&97248&5\\ 5275&97254&5\\ 5333& &2\\ 5333&24873&2\\ 5333&31479&2\\ 5333&34875&2\\ 5333&39875&2\\ 5333&54781&2\\ 5333&64817&2\\ 5333&64825&2\\ 5333&67128&2\\ 5333&69752&2\\ 5333&84785&2\\ 5333&97248&2\\ 
        \hline
        \end{tabular}
    }
}

\NEW{Label}{\sAnodyneTerminalFive}{
    \s\MYname   {Evidence Terminal 5/8}
    \s\MYloc    {}
    \s\MYtext   {
        \centering
        \begin{tabular}{|c|c||c|}
        \hline
        \bf A/I/S & \bf C & \bf E \\
        \hline
5333&97254&2\\ 5710& &5\\ 5710&24873&5\\ 5710&31479&5\\ 5710&34875&5\\ 5710&39875&5\\ 5710&54781&5\\ 5710&64817&5\\ 5710&64825&5\\ 5710&67128&5\\ 5710&69752&5\\ 5710&84785&5\\ 5710&97248&5\\ 5710&97254&5\\ 5785& &5\\ 5785&24873&5\\ 5785&31479&5\\ 5785&34875&5\\ 5785&39875&5\\ 5785&54781&5\\ 5785&64817&5\\ 5785&64825&5\\ 5785&67128&5\\ 5785&69752&5\\ 5785&84785&5\\ 5785&97248&5\\ 5785&97254&5\\ 6757& &5\\ 6757&24873&5\\ 6757&31479&5\\ 6757&34875&5\\ 6757&39875&5\\ 6757&54781&5\\ 6757&64817&5\\ 6757&64825&5\\ 6757&67128&5\\ 6757&69752&5\\ 6757&84785&5\\ 6757&97248&5\\ 6757&97254&5\\ 
        \hline
        \end{tabular}
        \quad
        \begin{tabular}{|c|c||c|}
        \hline
        \bf A/I/S & \bf C & \bf E \\
        \hline
7173& &5\\ 7173&24873&5\\ 7173&31479&5\\ 7173&34875&5\\ 7173&39875&5\\ 7173&54781&5\\ 7173&64817&5\\ 7173&64825&5\\ 7173&67128&5\\ 7173&69752&5\\ 7173&84785&5\\ 7173&97248&5\\ 7173&97254&5\\ 7188& &5\\ 7188&24873&5\\ 7188&31479&5\\ 7188&34875&5\\ 7188&39875&5\\ 7188&54781&5\\ 7188&64817&5\\ 7188&64825&5\\ 7188&67128&5\\ 7188&69752&5\\ 7188&84785&5\\ 7188&97248&5\\ 7188&97254&5\\ 7249& &5\\ 7249&24873&5\\ 7249&31479&5\\ 7249&34875&5\\ 7249&39875&5\\ 7249&54781&5\\ 7249&64817&5\\ 7249&64825&5\\ 7249&67128&5\\ 7249&69752&5\\ 7249&84785&5\\ 7249&97248&5\\ 7249&97254&5\\ 7280& &5\\ 
        \hline
        \end{tabular}
        \quad
        \begin{tabular}{|c|c||c|}
        \hline
        \bf A/I/S & \bf C & \bf E \\
        \hline
7280&24873&5\\ 7280&31479&5\\ 7280&34875&5\\ 7280&39875&5\\ 7280&54781&5\\ 7280&64817&5\\ 7280&64825&5\\ 7280&67128&5\\ 7280&69752&5\\ 7280&84785&5\\ 7280&97248&5\\ 7280&97254&5\\ 7690& &5\\ 7690&24873&5\\ 7690&31479&5\\ 7690&34875&5\\ 7690&39875&5\\ 7690&54781&5\\ 7690&64817&5\\ 7690&64825&5\\ 7690&67128&5\\ 7690&69752&5\\ 7690&84785&5\\ 7690&97248&5\\ 7690&97254&5\\ 7694& &5\\ 7694&24873&5\\ 7694&31479&5\\ 7694&34875&5\\ 7694&39875&5\\ 7694&54781&5\\ 7694&64817&5\\ 7694&64825&5\\ 7694&67128&5\\ 7694&69752&5\\ 7694&84785&5\\ 7694&97248&5\\ 7694&97254&5\\ 7742& &5\\ 7742&24873&5\\ 
        \hline
        \end{tabular}
    }
}

\NEW{Label}{\sAnodyneTerminalSix}{
    \s\MYname   {Evidence Terminal 6/8}
    \s\MYloc    {}
    \s\MYtext   {
        \centering
        \begin{tabular}{|c|c||c|}
        \hline
        \bf A/I/S & \bf C & \bf E \\
        \hline
7742&31479&5\\ 7742&34875&5\\ 7742&39875&5\\ 7742&54781&5\\ 7742&64817&5\\ 7742&64825&5\\ 7742&67128&5\\ 7742&69752&5\\ 7742&84785&5\\ 7742&97248&5\\ 7742&97254&5\\ 8300& &5\\ 8300&24873&5\\ 8300&31479&5\\ 8300&34875&5\\ 8300&39875&5\\ 8300&54781&5\\ 8300&64817&5\\ 8300&64825&5\\ 8300&67128&5\\ 8300&69752&5\\ 8300&84785&5\\ 8300&97248&5\\ 8300&97254&5\\ 8324& &5\\ 8324&24873&5\\ 8324&31479&5\\ 8324&34875&5\\ 8324&39875&5\\ 8324&54781&5\\ 8324&64817&5\\ 8324&64825&5\\ 8324&67128&5\\ 8324&69752&5\\ 8324&84785&5\\ 8324&97248&5\\ 8324&97254&5\\ 8348& &5\\ 8348&24873&5\\ 8348&31479&5\\ 
        \hline
        \end{tabular}
        \quad
        \begin{tabular}{|c|c||c|}
        \hline
        \bf A/I/S & \bf C & \bf E \\
        \hline
8348&34875&5\\ 8348&39875&5\\ 8348&54781&5\\ 8348&64817&5\\ 8348&64825&5\\ 8348&67128&5\\ 8348&69752&5\\ 8348&84785&5\\ 8348&97248&5\\ 8348&97254&5\\ 8511& &5\\ 8511&24873&5\\ 8511&31479&5\\ 8511&34875&5\\ 8511&39875&5\\ 8511&54781&5\\ 8511&64817&5\\ 8511&64825&5\\ 8511&67128&5\\ 8511&69752&5\\ 8511&84785&5\\ 8511&97248&5\\ 8511&97254&5\\ 8703& &5\\ 8703&24873&5\\ 8703&31479&5\\ 8703&34875&5\\ 8703&39875&5\\ 8703&54781&5\\ 8703&64817&5\\ 8703&64825&5\\ 8703&67128&5\\ 8703&69752&5\\ 8703&84785&5\\ 8703&97248&5\\ 8703&97254&5\\ 8745& &2\\ 8745&24873&2\\ 8745&31479&2\\ 8745&34875&2\\ 
        \hline
        \end{tabular}
        \quad
        \begin{tabular}{|c|c||c|}
        \hline
        \bf A/I/S & \bf C & \bf E \\
        \hline
8745&39875&2\\ 8745&54781&2\\ 8745&64817&2\\ 8745&64825&2\\ 8745&67128&2\\ 8745&69752&2\\ 8745&84785&2\\ 8745&97248&2\\ 8745&97254&2\\ 8772& &5\\ 8772&24873&5\\ 8772&31479&5\\ 8772&34875&5\\ 8772&39875&5\\ 8772&54781&5\\ 8772&64817&5\\ 8772&64825&5\\ 8772&67128&5\\ 8772&69752&5\\ 8772&84785&5\\ 8772&97248&5\\ 8772&97254&5\\ 8827& &5\\ 8827&24873&5\\ 8827&31479&5\\ 8827&34875&5\\ 8827&39875&5\\ 8827&54781&5\\ 8827&64817&5\\ 8827&64825&5\\ 8827&67128&5\\ 8827&69752&5\\ 8827&84785&5\\ 8827&97248&5\\ 8827&97254&5\\ 9221& &5\\ 9221&24873&5\\ 9221&31479&5\\ 9221&34875&5\\ 9221&39875&5\\ 
        \hline
        \end{tabular}
    }
}

\NEW{Label}{\sAnodyneTerminalSeven}{
    \s\MYname   {Evidence Terminal 7/8}
    \s\MYloc    {}
    \s\MYtext   {
        \centering
        \begin{tabular}{|c|c||c|}
        \hline
        \bf A/I/S & \bf C & \bf E \\
        \hline
9221&54781&5\\ 9221&64817&5\\ 9221&64825&5\\ 9221&67128&5\\ 9221&69752&5\\ 9221&84785&5\\ 9221&97248&5\\ 9221&97254&5\\ 9221& &5\\ 9221&24873&5\\ 9221&31479&5\\ 9221&34875&5\\ 9221&39875&5\\ 9221&54781&5\\ 9221&64817&5\\ 9221&64825&5\\ 9221&67128&5\\ 9221&69752&5\\ 9221&84785&5\\ 9221&97248&5\\ 9221&97254&5\\ 9226& &5\\ 9226&24873&5\\ 9226&31479&5\\ 9226&34875&5\\ 9226&39875&5\\ 9226&54781&5\\ 9226&64817&5\\ 9226&64825&5\\ 9226&67128&5\\ 9226&69752&5\\ 9226&84785&5\\ 9226&97248&5\\ 9226&97254&5\\ 9242& &5\\ 9242&24873&5\\ 9242&31479&5\\ 9242&34875&5\\ 9242&39875&5\\ 9242&54781&5\\ 
        \hline
        \end{tabular}
        \quad
        \begin{tabular}{|c|c||c|}
        \hline
        \bf A/I/S & \bf C & \bf E \\
        \hline
9242&64817&5\\ 9242&64825&5\\ 9242&67128&5\\ 9242&69752&5\\ 9242&84785&5\\ 9242&97248&5\\ 9242&97254&5\\ 9246& &5\\ 9246&24873&5\\ 9246&31479&5\\ 9246&34875&5\\ 9246&39875&5\\ 9246&54781&5\\ 9246&64817&5\\ 9246&64825&5\\ 9246&67128&5\\ 9246&69752&5\\ 9246&84785&5\\ 9246&97248&5\\ 9246&97254&5\\ 9253& &5\\ 9253&24873&5\\ 9253&31479&5\\ 9253&34875&5\\ 9253&39875&5\\ 9253&54781&5\\ 9253&64817&5\\ 9253&64825&5\\ 9253&67128&5\\ 9253&69752&5\\ 9253&84785&5\\ 9253&97248&5\\ 9253&97254&5\\ 9259& &5\\ 9259&24873&5\\ 9259&31479&5\\ 9259&34875&5\\ 9259&39875&5\\ 9259&54781&5\\ 9259&64817&5\\ 
        \hline
        \end{tabular}
        \quad
        \begin{tabular}{|c|c||c|}
        \hline
        \bf A/I/S & \bf C & \bf E \\
        \hline
9259&64825&5\\ 9259&67128&5\\ 9259&69752&5\\ 9259&84785&5\\ 9259&97248&5\\ 9259&97254&5\\ 9779& &5\\ 9779&24873&5\\ 9779&31479&5\\ 9779&34875&5\\ 9779&39875&5\\ 9779&54781&5\\ 9779&64817&5\\ 9779&64825&5\\ 9779&67128&5\\ 9779&69752&5\\ 9779&84785&5\\ 9779&97248&5\\ 9779&97254&5\\ 9817& &5\\ 9817&24873&5\\ 9817&31479&5\\ 9817&34875&5\\ 9817&39875&5\\ 9817&54781&5\\ 9817&64817&5\\ 9817&64825&5\\ 9817&67128&5\\ 9817&69752&5\\ 9817&84785&5\\ 9817&97248&5\\ 9817&97254&5\\ 9819& &5\\ 9819&24873&5\\ 9819&31479&5\\ 9819&34875&5\\ 9819&39875&5\\ 9819&54781&5\\ 9819&64817&5\\ 9819&64825&5\\ 
        \hline
        \end{tabular}
    }
}

\NEW{Label}{\sAnodyneTerminalEight}{
    \s\MYname   {Evidence Terminal 8/8}
    \s\MYloc    {}
    \s\MYtext   {
        \centering
        \begin{tabular}{|c|c||c|}
        \hline
        \bf A/I/S & \bf C & \bf E \\
        \hline
9819&67128&5\\ 9819&69752&5\\ 9819&84785&5\\ 9819&97248&5\\ 9819&97254&5\\ 9820& &2\\ 9820&24873&2\\ 9820&31479&2\\ 9820&34875&2\\ 9820&39875&2\\ 9820&54781&2\\ 9820&64817&2\\ 9820&64825&2\\ 9820&67128&2\\ 9820&69752&2\\ 9820&84785&2\\ 9820&97248&2\\ 9820&97254&2\\ 
        \hline
        \end{tabular}
    }
}

\NEW{LabelSmall}{\sEvidenceEnvelopeOne}{
	\s\MYname	{Evidence Type 1}
	\s\MYloc	{}
	\s\MYtext	{After placing the third (or greater) recording in this envelope, open and read the next page.}
}

\NEW{LabelSmall}{\sEvidenceEnvelopeOneTrigger}{
	\s\MYname	{Proof of Illegal Activity Collected}
	\s\MYloc	{}
	\s\MYtext	{You have collected enough evidence of cult activity, hacking, sabotage, or attempted murder aboard \emph{TIS Chivalry} to impound the ship.}
}

\NEW{LabelSmall}{\sEvidenceEnvelopeTwo}{
	\s\MYname	{Evidence Type 2}
	\s\MYloc	{}
	\s\MYtext	{After placing the third (or greater) recording in this envelope, open and read the next page.}
}

\NEW{LabelSmall}{\sEvidenceEnvelopeTwoTrigger}{
	\s\MYname	{Proof of Captivity Collected}
	\s\MYloc	{}
	\s\MYtext	{You have collected enough evidence of unfair wages, enslavement, or human cargo aboard \emph{TIS Chivalry} to impound the ship.}
}

\NEW{LabelSmall}{\sEvidenceEnvelopeThree}{
	\s\MYname	{Evidence Type 3}
	\s\MYloc	{}
	\s\MYtext	{After placing the third (or greater) recording in this envelope, open and read the next page.}
}

\NEW{LabelSmall}{\sEvidenceEnvelopeThreeTrigger}{
	\s\MYname	{Proof of Corrupt Officer Collected}
	\s\MYloc	{}
	\s\MYtext	{You have collected enough evidence to charge \cCbad{} with corruption.}
}

\NEW{LabelSmall}{\sEvidenceEnvelopeFour}{
	\s\MYname	{Evidence Type 4}
	\s\MYloc	{}
	\s\MYtext	{After placing the third (or greater) recording in this envelope, open and read the next page.}
}

\NEW{LabelSmall}{\sEvidenceEnvelopeFourTrigger}{
	\s\MYname	{Proof of Parole Violation Collected}
	\s\MYloc	{}
	\s\MYtext	{You have collected enough evidence to charge \cPilot{} with violating parole.}
}

\NEW{LabelSmall}{\sEvidenceEnvelopeFive}{
	\s\MYname	{Evidence Type 5}
	\s\MYloc	{}
	\s\MYtext	{After placing the third (or greater) recording in this envelope, open and read the next page.}
}

\NEW{LabelSmall}{\sEvidenceEnvelopeFiveTrigger}{
	\s\MYname	{Hobbyist Videographer}
	\s\MYloc	{}
	\s\MYtext	{Congratulations, you have collected a bunch of worthless footage that is proof of absolutely nothing. Taxpayers will be happy to know that this is how Frith's Finest spends their time on duty.}
}

\NEW{LabelSmall}{\sEvidenceEnvelopeSix}{
	\s\MYname	{Evidence Type 6}
	\s\MYloc	{}
	\s\MYtext	{After placing the third (or greater) recording in this envelope, open and read the next page.}
}

\NEW{LabelSmall}{\sEvidenceEnvelopeSixTrigger}{
	\s\MYname	{Proof of Corrupt Officer Collected}
	\s\MYloc	{}
	\s\MYtext	{You have collected enough evidence to charge \cCgood{} with corruption.}
}

\NEW{Sign}{\sAnodyneWeaponsLocker}{
	\s\MYname	{Weapons Locker}
	\s\MYloc	{}
	\s\MYtext	{A compartment locked by a numeric keypad. You can only open this if you know the unlock code.}
}

\NEW{Sign}{\sLSRepair}{
	\s\MYname	{Requirements to restart Life Support}
	\s\MYloc	{}
	\s\MYtext	{Within this room are four tasks required to by pass the safety mechanisms around the parts to the restart key, each must be at least attempted by a different person per task. Taskes must be done one at a time. Once all tasks are complete place the parts thus retreived end into end and touch to this sign for a 5 count}
}

\NEW{Sign}{\sLSTaskOne}{
	\s\MYname	{Task One}
	\s\MYloc	{}
	\s\MYtext	{The first item needed to fix the Life Support requires undoing each of the knots protecting it, cutting the rope is not allowed }
}

\NEW{Sign}{\sLSTaskTwo}{
	\s\MYname	{Task Two}
	\s\MYloc	{}
	\s\MYtext	{The second item needed to fix the Life Support requires removal of the rubber bands, breaking a band suffers a 30 second penalty}
	}
\NEW{Sign}{\sLSTaskThree}{
	\s\MYname	{Task Three}
	\s\MYloc	{}
	\s\MYtext	{The Third item needed to fix the Life Support requires usage of the belts provided to 'fish' the part from one end of a narrow area demarked with tape on the ground. The person must be sitting on the X marked on the floor during the task.}
}
\NEW{Sign}{\sLSTaskFour}{
	\s\MYname	{Task Four}
	\s\MYloc	{}
	\s\MYtext	{The Fourth item needed to fix the Life Support requires the disarming of a copper plated device through the cutting of three appropriate colored bands on the side of the device, after which the bands across the opening may be removed. Tools for access have been provided. The bands are layed out in four distinct layers, each separated by a thick band that wrapps the whole device. \begin{itemize} 
			\item Inner Core that is under all of the bands. 
			\item Outer Core that is under all but one thick band. 
			\item Inner Casing, underneath the outer thick band. 
			\item Outer Casing, outide all three thick bands. 
		\end{itemize}
			First little slice, 
			
			so easy so nice. 
			
			Outermost level gets the sun. 
			
			That color of the sun munchers is the one.
			
			Second cut so new
			
			Deeper, deeper, deepest be where
			
			the needed band so blue
			
			that needs be snipped with care.
			
			Triple play doth be
			
			next out one level so lovely.
			
			Slice the healthy pallor 
			
			before you lose your
			
			support of the lively.}
}

\NEW{Sign}{\sVoneTerminalLoggedOut}{
	\s\MYname	{Computer Terminal for Konrad von Manfred (Logged Out)}
	\s\MYloc	{}
	\s\MYtext	{A monitor, a keyboard, and a dock for connecting portable devices. If you own this terminal, you can read the next sheet without hacking. Hacking Difficulty 2}
	\s\MYitems{\iBlackMailD{}}
}

\NEW{Sign}{\sVoneTerminalLoggedIn}{
	\s\MYname	{Computer Terminal for Konrad von Manfred (Logged In)}
	\s\MYloc	{}
	\s\MYtext	{Within are several files. Of particular importance is on file detailing past deals. You may copy this by spending 1 minute accessing this terminal, followed by removing an item from the packet underneath this sign. The item is infinite in supply, if it is out please ask a GM.}
	\s\MYitems {\multi{5}{\iBlackMailD{}}}
}

\NEW{Sign}{\sVtwoTerminalLoggedOut}{
	\s\MYname	{Computer Terminal for Markus de Asad (Logged Out)}
	\s\MYloc	{}
	\s\MYtext	{A monitor, a keyboard, and a dock for connecting portable devices. If you own this terminal, you can read the next sheet without hacking. Hacking Difficulty 2}
}

\NEW{Sign}{\sVtwoTerminalLoggedIn}{
	\s\MYname	{Computer Terminal for Markus de Asad (Logged In)}
	\s\MYloc	{}
	\s\MYtext	{Within are several files. Of particular importance is on file detailing recordings of the ghouling of past crew members against their will. You may copy this by spending 1 minute accessing this terminal, followed by removing an item from the packet underneath this sign. The item is infinite in supply, if it is out please ask a GM.}
	\s\MYitems{\multi{5}{\iGhoulVid{}}}
}

\NEW{Sign}{\sVthreeTerminalLoggedOut}{
	\s\MYname	{Computer Terminal for Isabella das Scherer (Logged Out)}
	\s\MYloc	{}
	\s\MYtext	{A monitor, a keyboard, and a dock for connecting portable devices. If you own this terminal, you can read the next sheet without hacking. Hacking Difficulty 2}
}

\NEW{Sign}{\sVthreeTerminalLoggedIn}{
	\s\MYname	{Computer Terminal for Isabella das Scherer (Logged In)}
	\s\MYloc	{}
	\s\MYtext	{Within are several files. Of particular importance is one file detailing how one would fix the, in the owner's opinion, sad excuse for equipment that \cJames{} uses. You may copy this by spending 1 minute accessing this terminal, followed by removing an item from the packet underneath this sign. The item is infinite in supply, if it is out please ask a GM.}
	\s\MYitems{\multi{5}{\iInformation{}}}
}

\NEW{Sign}{\sCentrifugeBroken}{
	\s\MYname	{Centrifuge (Broken)}
	\s\MYloc	{}
	\s\MYtext	{A broken centrifuge. If you manage to fix this, tear off this sheet.}
}

\NEW{Sign}{\sCentrifuge}{
	\s\MYname	{Centrifuge}
	\s\MYloc	{}
	\s\MYtext	{A centrifuge.}
}

\NEW{Sign}{\sLockedBox}{
	\s\MYname	{Isotope Storage Box (Closed)}
	\s\MYloc	{}
	\s\MYtext	{This box is locked tight. To open it, attack it with a combined CR of 6. Then tear off this sheet.}
}

\NEW{Sign}{\sBox}{
	\s\MYname	{Isotope Storage Box (Open)}
	\s\MYloc	{}
	\s\MYtext	{A box made to store isotopes. To remove an isotope, put your hand on the box for an interruptible 5-count. You may only take one out every 15 minutes.}
	\s\MYitems {\multi{3}{\iIsotope{}}}
}

\NEW{Sign}{\sWrenchSign}{
	\s\MYname	{Box of Wrenches}
	\s\MYloc	{}
	\s\MYtext	{A toolbox full of wrenches. To take one out, put your hand on this sign for 30 seconds. You may take one out every 15 minutes.}
	\s\MYitems {\multi{3}{\iWrench{}}}
}

\NEW{Sign}{\sChemVRack}{
	\s\MYname	{Rack of Chemical V}
	\s\MYloc	{}
	\s\MYtext	{A rack of test tubes of \iChemicalV{}. To take one out, put your hand on this sign for 30 seconds. You may take one out every 15 minutes.}
	\s\MYitems {\multi{3}{\iChemicalV{}}}
}

\NEW{Sign}{\sWireSign}{
	\s\MYname	{Box of Wires}
	\s\MYloc	{}
	\s\MYtext	{A box of miscellaneous wires. To take a bundle out, put your hand on this sign for 30 seconds. You may take one bundle out every 15 minutes.}
	\s\MYitems {\multi{3}{\iWires{}}}
}

\NEW{Sign}{\sYPack}{
	\s\MYname	{Y Packet}
	\s\MYloc	{}
	\s\MYtext	{This is an Out of Game Packet for retrieval of relevant things}
	\s\MYitems {\multi{6}{\iInvisibilityCloak{}\iCRUpPotion{}\iHealthPotion{}\iBlackMailD{}}}
	\s\MYabils {\multi{6}{\aOpenWay{}\aHolyHands{}}}
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
