\documentclass[green]{guildcamp4}
\begin{document}
\name{\gDuel{}}

If you have this sheet, it means you know the proper procedure for dueling. You may verbally share these instructions with anyone with whom you wish to duel, after which they will be able to participate. The duel will only be valid if you provide correct instructions.

In order to duel, you and your opponent must first have rapiers. If you wish to duel someone, approach them and ask them whether they would consent to a duel. Then you must set your wager, which determines what the winner of the duel receives. This could be anything from money to favors to positions of power, but at bare minimum you must set what each person will give to or do for the other if they lose. Before you duel, you must write out the terms of the wager on paper and each sign it. If you lose the duel, you must provide what you set in your wager. This is a kludge.

To duel, begin with your weapons out, facing your partner within ZOC. Then you both turn around and take five steps forward, incanting the number of each step. On five, you turn around and proceed as if you were using Darkwater combat (e.g. "wound" + your CR). This will represent you charging with rapiers drawn. The person with the higher incanted CR wins the duel. There will be no effect to your status (e.g. you will not actually be wounded) after the completion of the duel. The winner will receive the agreed upon prize.

Initiator of the duel keeps both rapiers if they win. The challenged individual gets to keep one if they win.

\end{document}
