%%%%%
%%
%% Greensheets live in this directory.  This file doubles as a
%% latex'able example greensheet.
%%
%% _template.tex serves as a bare-bones template suitable for
%% copying when starting a new sheet.
%%
%% Greensheet macros (in ../Lists/green-LIST.tex, presumably) each
%% have a file that lives here.  The argument to \name{...} probably
%% should be the macro for the given greensheet, which will generate
%% the greensheet's name as specified in green-LIST.tex.  However, you
%% can also just use \name{Some Text} if you want.
%%
%%%%%

\documentclass[green]{guildcamp4}
\begin{document}

\name{\gEvidence{}}

You have a \iVideoCamera{\MYname}, which lets you make recordings. Recordings are either pictures of things, or videos of people doing things. 
	
\begin{enum}[Creating recordings]
    \item With one hand, make a circle and hold it up to your eye, as if looking through a telescope. Tell anyone who looks at you that you are holding up a camera.
    \item Look through the circle at either an object, or someone doing something, for a silent, interruptible five count. The activity or object must be recorded for the entire five count.
    \item If you recorded an object, write the number from its item card or sign on a blank item card.
    \item If you recorded an activity, ask the player out of game to show you the front of the ability card for what they were doing, or sign whose instructions they were following. Write the character's badge number and the ability or sign number on a blank item card.
    \item Place the recording in the camera's envelope.
\end{enum}

\begin{itemz}[Notes]
	\item You can only record one person at time. If you recorded an activity being performed by more than one character, you must pick one.
	\item The camera can only store up to 3 recordings at a time. If it is full, you must delete (destroy) a recording before starting a new one. 
	\item Cameras are biometrically locked to their owners. You may only open a camera's envelope if you are the owner.
	\item Cameras can be taken by other characters, but not used, erased, or destroyed. 
\end{itemz}
    
Your police cruiser, the \emph{HMS Anodyne}, has a terminal which can be used to upload recordings to the indestructible onboard flight recorder.

\begin{enum}[Uploading evidence]
	\item Connect your camera to the terminal with an audible, interruptible 5-count.
    \item Upload a recording with an audible, interruptible 15-count.
    \item Look up the item, ability, or sign number on the attached sheet. Place the recording in the specified evidence envelope.    
    \item Resolve any instructions on the evidence envelope.
\end{enum}

\begin{itemz}[Notes]
	\item Evidence held on the flight recorder will be automatically transmitted to other Frith ships within broadcast range, if any.
\end{itemz}

\end{document}
