\documentclass[green]{Pestilence}
\begin{document}
\name{\gInfection{}}

The disease that is ravaging the streets outside is unlike anything recorded in medical literature. Some believe it to be a hyper-virulent hemorrhagic fever, while others gave it more mystical names such as blood rot or earth's death. It has no incubation period; affected individuals show obvious symptoms immediately, up to and including fever, fatigue, nausea, swollen joints, purple spots and bloodshot eyes. There is no widely known vaccine or cure at present. The disease usually kills after five hours.

The game will end in three hours, so no one who is infected during game will die during game solely from the disease. However, the army will refuse to save those who display signs of infection, and the infected will die shortly if they end the game untreated.

Stickers are in game information that represent infection. If you see a sticker on anyone, it means they are showing symptoms of the plague, even if they are not yet aware of the fact. You may or may not choose to tell players that they are infected. Once a player is aware that they are infected, they must put a sticker on their name badges. Their CR is reduced by 2 as long as they are infected. CR cannot go lower than 0.

NPCs can also be infected. An NPC sheet with a sticker on it denotes an infected townsperson.

Dead bodies are dangerous, especially if they belonged to infected people. The dead body of an infected person (NPC sign with an X and a sticker on it, or an abandoned name badge with a sticker) will immediately infect anyone who is within one ZOC of it without a mask. Matches are freely available, but fuel is required to burn these bodies. In general, be wary of dead bodies. Stickers and signs of infection are both hard to see from distance.

Infection has some perks if you are the vengeful type. Once you're aware you're infected, you may choose to take a Spread Plague ability card and an accompanying sheet of stickers from Envelope Z. A restrained plaguebearer is not capable of walking away, but they are still capable of infecting you if you are within arm's reach of them. 

If you see someone trying to infect you, you can prevent that by saying "I stop you" and moving out of the plaguebearer's reach within 5 seconds. The plaguebearer is not allowed to chase down people who escape them this way. However, if you say "I stop you" and remain within the plaguebearer's reach for more than 5 seconds, the plaguebearer can still infect you. You cannot interrupt a plaguebearer's attempt to infect another person; you can only warn the victim.    

\end{document}
