\documentclass[green]{Pestilence}
\begin{document}
\name{\gMercy{}}

You may have destroyed innocent lives in your panic. If so, you must help the town once you regain your powers. Else, you might have exacted righteous vengeance on a corrupt town. In this case, you are under no obligation to aid anyone once your powers are restored.

Your view of the town is determined by your Mercy score. You start out with 0 Mercy. If your Mercy is greater than 15 when your power is restored, you will aid the sick. If your Mercy is less than or equal to 15, you are free to choose who lives and who dies. 

If your Mercy dips to -15, you are enraged and you will spread as much infection as possible until the score is raised above -15. Mercy cannot go below -15. \cShaman{} may be exempt from your rage unless you want it otherwise.

Acts that increase your Mercy include:

\begin{itemz}
	\item Someone protects you or \cShaman{} from physical harm (+1)
	\item Someone plays with you. You love human games! (+1)
	\item Someone gives you gifts (+1)
	\item Someone defends your reputation (+1)
	\item Someone declares their care for someone else (+1)
	\item Someone stops a killing blow (+2)
	\item Someone is willing to sacrifice themselves for your ritual (+2, once for each willing individual you encounter)
	\item The ritual to restore your power is completed with a willing sacrifice (+5, regardless of success)
	\item\cElder{\intro} is sacrificed for your ritual (+10, stacks with above)
\end{itemz}

Acts that decrease your Mercy include:

\begin{itemz}
	\item Someone insults you or \cShaman{} (-1)
	\item Someone doubts the powers of the earth (-1)
	\item Anyone who is not you spreads infection (-2 for each infected)
	\item You hear rumors and stories that involve murder. Righteous sacrifice is not murder (-2)
	\item You witness drawing of blood (-2)
	\item You witness burning of bodies (-2)
	\item Someone you infected is cured. Only you are allowed to rescind your punishment (-3)
	\item Anyone attacks you or \cShaman{} (-3)
	\item You witness a murder (-5)
	\item \cShaman{} is killed (-10, stacks with above)
\end{itemz}

You are encouraged to be proactive in determining whether or not the town is worthy of your mercy. Men often show their true nature under pressure. Give them opportunities where they can choose to either save or destroy each other.

\end{document}
