\documentclass[green]{guildcamp4}
\begin{document}
\name{\gSabotage{}}

\emph{(This greensheet details how to attempt to sabotage a engine.)}

Engines are susceptible to being sabotaged. Sabotage is a delicate and often time consuming process. The difficulty of sabotaging an engine depends on the engine itself. If anyone observes you while in this process, you must tell them that you are fiddling with the engine in an obvious attempt to break it.\\

How to sabotage an engine:
\begin{enumerate}
	\item Shuffle the deck seven times.
	\item Deal out 2 cards. This is your {\em working hand}.
	\item Deal out 5 cards in a line above your working hand. This is your {\em dynamic library}.
	\item You may swap out a card in your working hand with a card in your dynamic library.
	\item Check to see if you can make a straight of the required size from the cards in your working hand and dynamic library. If not, discard your dynamic library.
	\item Repeat steps 3-5 until you have fulfilled your success condition or you run through the deck.  If you run out of deck, you must start over from step 1.
\end{enumerate}

{\bf Success Condition by Engine Difficulty:}\\

\begin{tabular}{||r|l||}
	\hline\hline
	Engine Difficulty	& Required hand\\
	\hline
	0	& Straight of 4\\
	1	& Straight of 5\\
	2	& Straight of 6\\
	3	& Straight of 7\\
	4	& Straight of 8\\
	\hline\hline 
\end{tabular}

\vspace{10 mm}

Aces can count as high or low, but wrapping is not allowed. (IE: Q, K, A, 2, 3 is {\bf not} a valid 5 card straight.)

You may notice that several engines start out impossible. This is intentional. If you attempt to hack a terminal and fail (by running out of deck), you may try again immediately (continue the session), or you may give up (end the session). If you have tried to sabotage an engine twice in the same session, the third time you try to sabotage an engine in the same session, you may reduce the engine difficulty by 1. Failing twice with the new difficulty will allow you to reduce it further, and so on, down to a minimum of 0.

There may be other ways to reduce the difficulty of an engine.

\end{document}
