\documentclass[green]{guildcamp4}
\begin{document}
\name{\gSins{}}

If you have this sheet, it means that you care about whether actions are sins or good works. Use this as a reference to determine whether an act is a sin or good work. Interpret this as you will. If you have a question about whether something is a sin or good work and it isn't on this list, ask a GM.

\begin{center}{\bf Sins}\end{center}

\begin{itemz}[Breaking the Ten Commandments:]
	\item 1. I am the LORD your God: you shall not have strange Gods before me.
	\item 2. You shall not take the name of the LORD your God in vain.
	\item 3. Remember to keep holy the LORD'S Day.
	\item 4. Honor your father and your mother.
	\item 5. You shall not kill.
	\item 6. You shall not commit adultery.
	\item 7. You shall not steal.
	\item 8. You shall not bear false witness against your neighbor.
	\item 9. You shall not covet your neighbor's wife.
	\item 10. You shall not covet your neighbor's goods.
\end{itemz}

\begin{itemz}[The Seven Deadly Sins:]
	\item Pride
	\item Envy
	\item Wrath
	\item Gluttony
	\item Lust
	\item Sloth
	\item Greed
\end{itemz}

\begin{itemz}[Miscellaneous Sins:]
	\item Blood magic/"science"
	\item Making someone a ghoul
	\item Bribery or blackmail
\end{itemz}

\begin{center}{\bf Good Works}\end{center}

\begin{itemz}[Corporal Works of Mercy:]
	\item 1. To feed the hungry.
	\item 2. To give drink to the thirsty.
	\item 3. To clothe the naked.
	\item 4. To shelter the homeless.
	\item 5. To visit the sick.
	\item 6. To visit the imprisoned.
	\item 7. To bury the dead.
\end{itemz}

\begin{itemz}[Spiritual Works of Mercy:]
	\item 1. To instruct the ignorant.
	\item 2. To counsel the doubtful.
	\item 3. To admonish sinners.
	\item 4. To bear wrongs patiently.
	\item 5. To forgive offenses willingly.
	\item 6. To comfort the afflicted.
	\item 7. To pray for the living and the dead.
\end{itemz}

\begin{itemz}[Miscellaneous Good Works:]
	\item Freeing the imprisoned.
	\item Protecting the innocent.
	\item Preventing unnecessary violence.
	\item Prayer to God/Jesus.
	\item Blessing a person with holy water (same process as prayer, but requires holy water.)
	\item Assisting others in good works.
\end{itemz}

{\bf A Note on Prayer:}

In order to represent saying a prayer, incant an interruptible 20-count.

\end{document}
