\documentclass[green]{Pestilence}
\begin{document}
\name{\gTownsfolk{}}

The PCs are not the only ones in the shelter. Various townsfolk are also gathered throughout the shelter, represented by sheets on the wall. They are too fatigued to defend themselves or notice the PCs' actions. They are so traumatized by their losses and so hateful of the town healers for failing them that they will refuse to give blood or consent to any experimentation. You can murder each other in plain sight of all the NPCs, and none of them will care enough to notice or intervene.

Townsfolk can be infected, cured or killed. If you are infected, you may place a sticker on an NPC sheet to infect them. This sticker can be removed only if the townsperson is cured through an ability. Townsfolk generally distrust medicinal cures due to rumors of fake medicine being sold in the streets.

To kill an townsperson, put your hand on their sheet and start a 10-count interruptible killing blow, as you would with a PC. Unless you are explicitly unable to attack, you can kill a townsperson regardless of how low your CR is. Once you've killed a townsperson, draw a large, noticeable X on their sheet.

{\bf Playable Townsfolk}

Some runs may have a townsperson NPC portrayed by a real person as opposed to a sheet on the wall. Playable townsfolk obey the same rules as sheet on the wall townsfolk. They do not take items, notice sneaky actions, convey useful information, intervene in fights, consent to experiments or say nice things to healers. They cannot be wounded or knocked out, only killed, infected or cured through an ability.

If a playable townsperson is killed, they are allowed to swap places with a random sheet NPC once their death is publicly known. For instance, an infected playable townsperson is killed. They play their body for five minutes and then swap places with a healthy sheet NPC by crossing out the sheet, putting a sticker on it, and putting the sheet where their body was. They can now play as a healthy townsperson with different mannerisms. If all the townsfolk are dead, playable townsfolk may return as a ghost. 

\end{document}
